---
title: "Study 3 data cleaning"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(scipen=999)
```

This script cleans the raw data from Study 3.

# load packages
```{r}
if (!require(tidyverse)) {
  install.packages('tidyverse')
}
if (!require(knitr)) {
  install.packages('knitr')
}
if (!require(DT)) {
  install.packages('DT')
}
if (!require(devtools)) {
  install.packages('devtools')
}
if (!require(scorequaltrics)) {
  devtools::install_github('dcosme/qualtrics', ref = "dev/enhance")
}
```

# load and tidy data {.tabset}
## define variables and paths

To pull data from Qualtrics directly, you need a credentials file with an API token associated with your account. To create the file, follow these steps.

1. Generate an API token for Qualtrics. Follow the steps outlined [here](https://www.qualtrics.com/support/integrations/api-integration/overview/).

2. Save a Qualtrics credentials text file with the following format. In this example, the file is being saved as `~/credentials.yaml.PENN`. The `baseurl` is the URL for your institution on Qualtrics. Use `upenn.co1.qualtrics.com` for Penn Qualtrics.

```
token: oILNW6...[your qualtrics API token]
baseurl: upenn.co1.qualtrics.com
```

`cred_file_location` = path to your Qualtrics credential file. 

`survey_name_filter` = regular expression to filter the available stuveys

```{r}
cred_file_location = '~/credentials.yaml.PENN'
survey_filter = 'PLTV.*SONA'
```

## filter matching surveys
```{r}
# load credential file
credentials = scorequaltrics::creds_from_file(cred_file_location)

# filter
surveysAvail = scorequaltrics::get_surveys()
surveysFiltered = filter(surveysAvail, grepl(survey_filter, name))
knitr::kable(arrange(select(surveysFiltered, name), name))
```

## load data
* The survey key is located [here]()
* The message stimuli can be found [here]())

```{r}
survey_raw = scorequaltrics::get_survey_responses(surveysFiltered$id[1])
```

## tidy data and select relevant variables
This code tidies the raw data and outputs a dataframe in the long format with the following columns:

`study` = study name  
`condition` = experimental group (no message control, message control, norm, autonomous, mocking)  
`survey_name` = name of the survey or question category (e.g. intentions or SES)  
`item` = individual survey item (or message rating) name  
`value` = response or rating  

```{r}
# load and tidy survey
surveys = survey_raw %>%
  filter(!DistributionChannel == "preview") %>% # remove preview responses
  filter(is.na(eligible)) %>% # remove participants who were ineligible
  filter(Progress >= 98) %>% # remove incomplete responses
  mutate(SID = sprintf("s%03d", row_number())) %>% # create unique SID
  gather(item, value, -c(SID, group)) %>%
  mutate(value = ifelse(value == "", NA, value), #recode blank values as NA
         item = gsub("message_ratings_e_|message_ratings_c_", "msg_", item),
         item = gsub("msg_1", "msg_rel_self", item),
         item = gsub("msg_2", "msg_rel_social", item),
         item = gsub("msg_3", "msg_motivation_self", item),
         item = gsub("msg_4", "msg_motivation_social", item),
         item = gsub("msg_5", "msg_sharing_broad", item),
         item = gsub("msg_6", "msg_sharing_narrow", item),
         item = gsub("msg_7", "msg_check_norms", item),
         item = gsub("msg_8", "msg_check_identity", item),
         item = gsub("([1-5])_(msg_.*)", "\\2_\\1", item)) %>%
  filter(!(is.na(value) & grepl("msg_", item))) %>% #remove items from the other experimental condition
  extract(item, "survey_name", "(.*)_[0-9]+", remove = FALSE) %>%
  mutate(survey_name = ifelse(is.na(survey_name), item, survey_name),
         survey_name = gsub("[0-9]+_", "", survey_name)) %>%
  filter(!grepl("_DO_", item)) %>% # remove randomization order info
  filter(grepl("msg_rel|msg_sharing|gender|race$|hispanic_latinx|student_grade", survey_name)) # filter relevant variables

# spread to wide format
surveys_wide = surveys %>%
  select(-survey_name) %>%
  spread(item, value)
```

# summarize survey ns
```{r}
surveys %>%
  select(SID) %>%
  unique() %>%
  summarize(n = n())

surveys %>%
  filter(!is.na(value)) %>%
  group_by(survey_name) %>%
  select(SID, survey_name) %>%
  unique() %>%
  summarize(n = n()) %>%
  DT::datatable(filter = "top", rownames = FALSE)
```

# write csvs
```{r}
write.csv(filter(surveys, !grepl("gender|race$|hispanic_latinx|student_grade", item)),
          "../data/study3_clean_long.csv", row.names = FALSE)
write.csv(filter(surveys, grepl("gender|race$|hispanic_latinx|student_grade", item)),
          "../data/study3_clean_long_demo.csv", row.names = FALSE)
```
