---
title: "Study 1d data cleaning"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(scipen=999)
```

This document provides the code for the analyses reported in:

[Cosme et al. (Preprint) Message self and social relevance is positively related to sharing intentions:
Correlational and causal evidence from six studies]()

This script cleans the raw data from Study 1d.

# load packages
```{r}
if (!require(tidyverse)) {
  install.packages('tidyverse')
}
if (!require(knitr)) {
  install.packages('knitr')
}
if (!require(DT)) {
  install.packages('DT')
}
if (!require(pander)) {
  install.packages('pander')
}
```

# load and tidy data

* The survey key is located [here](https://upenn.box.com/s/ftm9deaq4tqflzjxwhmboqy9q6c9dxpu)
* The message stimuli can be found [here](https://upenn.box.com/s/h3vhnqbdmp383rvahnaalas20cqz7u5g)

Note that the MIDs have been scrambled in the raw qualtrics data to deidentify them. Scrambling was conducted using the following code:

```
read.csv("covid19_study1_qualtrics.csv", stringsAsFactors = FALSE) %>% 
  mutate(MID = stringi::stri_rand_shuffle(MID)) %>%
  write.csv("covid19_study1_qualtrics.csv", row.names = FALSE)
```

This code tidies the raw data and outputs a dataframe in the long format with the following columns:

`condition` = experimental group (no mocking humor, non-mocking humor, fact-based)  
`survey_name` = name of the survey or question category (e.g. intentions or SES)  
`item` = individual survey item (or message rating) name  
`value` = response or rating  

```{r}
# load state codes
states = read.csv("state_codes.csv", stringsAsFactors = FALSE) %>%
  mutate(state_code = as.character(state_code))

# load message info
message_info = read.csv("../../../covid19-message-framing-private/humor/message_info.csv", stringsAsFactors = FALSE) %>%
  dplyr::rename("message_text" = text) %>%
  mutate(condition = gsub(" ", "", condition),
         condition = tolower(condition),
         condition = ifelse(condition == "fact-based", "fact-based",
                     ifelse(condition == "nonmockinghumor", "non-mocking",
                     ifelse(condition == "mockinghumor", "mocking", condition)))) %>%
  mutate(message = sprintf("msg_%02d", as.numeric(image_number))) %>%
  mutate(behavior = "social_distancing") %>%
  dplyr::select(condition, message, message_text, behavior)

# load and tidy survey
surveys = read.csv("../../../covid19-message-framing-private/humor/COVID-19 Humor Study_April 15, 2020_22.00.csv", stringsAsFactors = FALSE) %>%
  slice(3:n()) %>%
  filter(!DistributionChannel == "preview") %>% # remove preview responses
  filter(!mturk_code == "") %>% # remove participants who failed screener
  filter(!MID == "" | StartDate == "") %>% # remove test responses
  mutate(SID = sprintf("s%04d", row_number())) %>% # create unique SID
  dplyr::rename("schadenfreude_1" = shcadenfreude_1,
         "schadenfreude_2" = shcadenfreude_2,
         "schadenfreude_3" = shcadenfreude_3,
         "policy2_1" = policy_1,
         "policy2_2" = policy2_33,
         "policy2_3" = policy2_34,
         "policy2_4" = policy2_35) %>%
  dplyr::rename("policy_1" = policy_1.1) %>%
  gather(var, val, starts_with("X")) %>%
  tidyr::extract(var, c("message", "condition", "question"), "X([0-9]+)_(.*)_(msg.*)", remove = FALSE) %>% #rename conditions
  mutate(condition = ifelse(condition == "f", "fact-based",
                     ifelse(condition == "m", "mocking",
                     ifelse(condition == "n", "non-mocking",condition))),
         message = recode(message, "1" = "04", "2" = "07", "3" = "08", "4" = "12", "5" = "17"), # recode messages to match those in message_info.csv,
         var = sprintf("%s_%s_%s", condition, question, message)) %>%
  dplyr::select(-c(message, condition, question, MID), -contains(".stims")) %>%
  spread(var, val) %>%
  gather(item, value, -c(SID)) %>%
  mutate(value = ifelse(value == "", NA, value)) %>%
  tidyr::extract(item, "survey_name", "(.*)_[0-9]+", remove = FALSE) %>%
  mutate(survey_name = ifelse(is.na(survey_name), item, survey_name)) %>%
  filter(!grepl("pre_", item) & !grepl("post_", item))

# change choice text to numeric
surveys <- surveys %>%
  mutate(value = ifelse(survey_name %in% c("beliefs_mental", "beliefs_norms",
                                           "beliefs_environment", "beliefs_safe_self",
                                           "beliefs_safe_others", "beliefs_others_home"), 
                        recode(value, "1Strongly disagree" = "1", "7Strongly agree" = "7"), value)) %>%
  mutate(value = ifelse(survey_name == "schadenfreude", recode(value, "Strongly disagree" = "1",
                                                               "Disagree" = "2",
                                                               "Somewhat disagree" = "3",
                                                               "Neither agree nor disagree" = "4",
                                                               "Somewhat agree" = "5",
                                                               "Agree" = "6",
                                                               "Strongly agree" = "7"), value)) %>%
  mutate(value = ifelse(survey_name %in% c("policy1", "policy2"), recode(value, "Strongly disagree" = "1",
                                                               "Disagree" = "2",
                                                               "Somewhat disagree" = "3",
                                                               "Neither agree nor disagree" = "4",
                                                               "Somewhat agree" = "5",
                                                               "Agree" = "6",
                                                               "Strongly agree" = "7"), value)) %>%
  mutate(value = ifelse(survey_name == "policy", recode(value, "1Do not support at all"  = "1",
                                                        "7Support very much" = "7"), value)) %>%
  mutate(value = ifelse(survey_name == "empathy", recode(value, "1Does not describe me well"  = "1",
                                                        "5Describes me very well" = "5"), value)) %>%
  mutate(value = ifelse(grepl("msg_funny", item), recode(value, "Not at all funny"  = "1",
                                                         "A bit funny" = "2",
                                                         "Mildly funny" = "3",
                                                         "Somewhat funny" = "4",
                                                         "Fairly funny" = "5",
                                                         "Very funny" = "6",
                                                         "Extremely funny" = "7"), value)) %>% 
  mutate(value = ifelse(grepl("msg_rel_", item), recode(value, "Strongly disagree" = "1",
                                                               "Disagree" = "2",
                                                               "Somewhat disagree" = "3",
                                                               "Neither agree nor disagree" = "4",
                                                               "Somewhat agree" = "5",
                                                               "Agree" = "6",
                                                               "Strongly agree" = "7"), value)) %>% 
  mutate(value = ifelse(grepl("msg_motiv_", item), recode(value, "Strongly disagree" = "1",
                                                               "Disagree" = "2",
                                                               "Somewhat disagree" = "3",
                                                               "Neither agree nor disagree" = "4",
                                                               "Somewhat agree" = "5",
                                                               "Agree" = "6",
                                                               "Strongly agree" = "7"), value)) %>% 
  mutate(value = ifelse(grepl("msg_share", item), recode(value, "Strongly disagree" = "1",
                                                               "Disagree" = "2",
                                                               "Somewhat disagree" = "3",
                                                               "Neither agree nor disagree" = "4",
                                                               "Somewhat agree" = "5",
                                                               "Agree" = "6",
                                                               "Strongly agree" = "7"), value))

# get completed messages and remove condition info
messages = surveys %>%
  filter(grepl("msg", item)) %>%
  filter(!item == "msg_open") %>%
  filter(!is.na(value)) %>%
  tidyr::extract(item, "condition", "(.*)_msg.*", remove = FALSE) %>%
  mutate(item = gsub("(.*)_msg", "msg", item),
         survey_name = gsub("(.*)_msg", "msg", survey_name))

# get condition information
conditions = surveys %>%
  filter(grepl("msg", item)) %>%
  filter(!item == "msg_open") %>%
  filter(!is.na(value)) %>%
  tidyr::extract(item, "condition", "(.*)_msg.*", remove = FALSE) %>%
  dplyr::select(SID, condition) %>%
  unique()

# replace messages 
surveys_merged = surveys %>%
  merge(conditions, by = "SID") %>% # add condition information
  filter(!grepl("msg.*[0-9]{2}", item)) %>% # remove message ratings
  bind_rows(messages) %>% # replace message ratings with cleaned message ratings
  dplyr::select(SID, condition, survey_name, item, value)

# spread to wide format
surveys_merged_wide = surveys_merged %>%
  dplyr::select(-survey_name) %>%
  spread(item, value)
```

## quality checks
### failed checks
* Many more people failed the flattening the curve question than the COVID-19 or social distancing questions
* Because the survey emphasizes COVID-19 and social distancing, let's just use those items to determine failed checks
* The correct answer for the English check is the school bus, but let's be lenient and accept the truck as well

```{r}
# identify failed attention checks
failed_attn = surveys %>%
  filter(item == "attention_2" & !grepl("about social media|copy", tolower(value))) %>%
  dplyr::select(SID, value) %>%
  unique()

# identify failed English checks
failed_english = surveys %>%
  filter(item == "english") %>%
  filter(!grepl("bus|truck", tolower(value)) | SID %in% c("s1284", "s0058", "s0850")) %>% #these participants copied the sentence
  dplyr::select(SID, value) %>%
  unique()

# print number of failed checks
failed = surveys %>% 
  dplyr::select(SID) %>% 
  unique() %>% 
  mutate(failed_attention = ifelse(SID %in% failed_attn$SID, 1, 0), 
         failed_english = ifelse(SID %in% failed_english$SID, 1, 0), 
         `failed english & attention` = ifelse(failed_attention == 1 & failed_english == 1, 1, 0),
         `failed at least one check`  = ifelse(failed_attention == 1 | failed_english, 1, 0))

failed %>%
  gather(check, val, contains("fail")) %>% 
  filter(val == 1) %>% 
  group_by(check) %>% 
  dplyr::summarize(n = n(),
            `%` = round(n / nrow(failed) * 100, 1)) %>%
  arrange(desc(n)) %>%
  pander()
```

### durations
#### overall durations
```{r, fig.width = 12, fig.height=4}
# extracting duration data
dur_plot_data = surveys %>%
  filter(item == "Duration..in.seconds.") %>%
  mutate(duration_mins = as.numeric(value) / 60,
         less_than_10_mins = ifelse(duration_mins < 10, 1, 0)) %>%
  mutate(n = n(),
         median = median(duration_mins, na.rm = TRUE))

dur_plot_data %>%
  filter(duration_mins < 200) %>%
  ggplot(aes(duration_mins)) +
  geom_histogram(alpha = .5) +
  geom_freqpoly() +
  geom_vline(aes(xintercept = median)) +
  ggplot2::annotate("text", label = sprintf("Median = %s", round(unique(dur_plot_data$median), 1)), x = unique(dur_plot_data$median) + 10, y = 175) + 
  labs(x = "duration (minutes)") +
  theme_minimal()
```

#### print survey data for participants with durations < 10 mins
```{r}
fast_subs = dur_plot_data %>%
  filter(less_than_10_mins == 1)

surveys_merged_wide %>% 
  filter(SID %in% fast_subs$SID) %>%
  left_join(., dplyr::select(dur_plot_data, SID, duration_mins)) %>%
  dplyr::select(SID, duration_mins, everything()) %>%
  dplyr::select(-condition) %>%
  mutate(duration_mins = round(duration_mins, 1)) %>%
  arrange(duration_mins) %>%
  DT::datatable(rownames = FALSE, extensions = 'FixedColumns', options = list(scrollX = TRUE,
                                                                              scrollY = TRUE,
                                                                              fixedColumns = list(leftColumns = 2)))
```

### invariance
Goal is to identify participants who are responding the same way across all items within a survey

* Calculate the SD for each surevy for each individual
* Single item scales are not included
* If SD = 0, code as invariant and calculate the percentage of invariant surveys for each participant

```{r, fig.width = 8}
invariance = surveys %>%
  dplyr::select(SID, survey_name, value) %>%
  group_by(SID, survey_name) %>%
  dplyr::summarize(sd_survey = sd(as.numeric(value), na.rm = TRUE)) %>%
  filter(!is.na(sd_survey)) %>%
  group_by(SID) %>%
  mutate(completed_variance = ifelse(!(is.na(sd_survey) | is.nan(sd_survey)), 1, 0),
         n_survey = sum(completed_variance, na.rm = TRUE),
         invariant = ifelse(sd_survey == 0, 1, 0),
         sum_invariant = sum(invariant, na.rm = TRUE),
         percent_surveys_invariant = (sum_invariant / n_survey ) * 100) %>%
  dplyr::select(SID, survey_name, sd_survey, percent_surveys_invariant) %>%
  ungroup() %>%
  dplyr::select(SID, percent_surveys_invariant) %>%
  unique() %>%
  mutate(median = median(percent_surveys_invariant, na.rm = TRUE),
         uppersd2 = median + (2 * sd(percent_surveys_invariant, na.rm = TRUE)),
         uppersd3 = median + (3 * sd(percent_surveys_invariant, na.rm = TRUE)),
         greater_than_2sd_invariance = ifelse(percent_surveys_invariant > uppersd2, 1, 0),
         greater_than_3sd_invariance = ifelse(percent_surveys_invariant > uppersd3, 1, 0))

invariance %>%
  ggplot(aes(percent_surveys_invariant)) +
    geom_histogram(alpha = .5) +
    geom_freqpoly() +
    geom_vline(aes(xintercept = median)) +
    annotate("text", label = sprintf("Median = %s", round(unique(invariance$median), 1)), 
             x = unique(invariance$median) + 5, y = 220, size = 2.5) + 
    geom_vline(aes(xintercept = uppersd2), linetype = "dotted") +
    annotate("text", label = sprintf("+2 SD = %s", round(unique(invariance$uppersd2), 1)), 
             x = unique(invariance$uppersd2) + 5, y = 220, size = 2.5) + 
    geom_vline(aes(xintercept = uppersd3), linetype = "dotted") +
    annotate("text", label = sprintf("+3 SD = %s", round(unique(invariance$uppersd3), 1)), 
             x = unique(invariance$uppersd3) + 5, y = 220, size = 2.5) + 
    scale_x_continuous(breaks = seq(0, 100, 10)) +
    scale_y_continuous(breaks = seq(0, 240, 20)) +
    labs(x = "percent invariance across surveys") +
    theme_minimal()
```

#### print survey data for participants with invariance > 3 SDs from the median

```{r}
invariant_subs = invariance %>%
  filter(greater_than_3sd_invariance == 1)

surveys_merged_wide %>% 
  filter(SID %in% invariant_subs$SID) %>%
  left_join(., select(invariance, SID, percent_surveys_invariant)) %>%
  select(SID, percent_surveys_invariant, everything()) %>%
  select(-condition) %>%
  mutate(percent_surveys_invariant = round(percent_surveys_invariant, 1)) %>%
  arrange(desc(percent_surveys_invariant)) %>%
  rename("% invariant" = percent_surveys_invariant) %>%
  DT::datatable(rownames = FALSE, extensions = 'FixedColumns', options = list(scrollX = TRUE,
                                                                              fixedColumns = list(leftColumns = 1)))
```

### combine quality indicators
Quality indicators:

* Failed attention, English, and COVID-10 knowledge checks
* Duration < 10 mins
* Invariance > 3 SDs from the median

```{r}
quality_check_all = dur_plot_data %>%
  select(SID, duration_mins, less_than_10_mins) %>%
  left_join(., select(invariance, SID, percent_surveys_invariant, greater_than_3sd_invariance)) %>%
  left_join(., select(failed, SID, failed_attention, failed_english)) %>%
  gather(var, val, contains("fail"), contains("than")) %>%
  group_by(SID) %>%
  mutate(n_indicators = sum(val),
         duration_mins = round(duration_mins, 1),
         percent_surveys_invariant = round(percent_surveys_invariant, 1)) %>%
  spread(var, val) %>% 
  filter(n_indicators > 0) %>%
  arrange(desc(n_indicators)) 

quality_check_notime = dur_plot_data %>%
  select(SID, duration_mins) %>%
  left_join(., select(invariance, SID, percent_surveys_invariant, greater_than_3sd_invariance)) %>%
  left_join(., select(failed, SID, failed_attention, failed_english)) %>%
  gather(var, val, contains("fail"), contains("than")) %>%
  group_by(SID) %>%
  mutate(n_indicators = sum(val),
         duration_mins = round(duration_mins, 1),
         percent_surveys_invariant = round(percent_surveys_invariant, 1)) %>%
  spread(var, val) %>% 
  filter(n_indicators > 0) %>%
  arrange(desc(n_indicators)) 

quality_check_failed = failed %>%
  filter(`failed at least one check` == 1)

quality_check_all %>%
  DT::datatable(filter = "top", rownames = FALSE, extensions = 'FixedColumns', 
                options = list(scrollX = TRUE, fixedColumns = list(leftColumns = 2)))
```

Excluding all these participants results in excluding `r round(nrow(quality_check_all) / nrow(dur_plot_data) * 100, 1)`% of participants (n = `r nrow(quality_check_all)`)

Removing the duration as an exclusion criteria results in excluding `r round(nrow(quality_check_notime) / nrow(dur_plot_data) * 100, 1)`% of participants (n = `r nrow(quality_check_notime)`)

Just excluding based on failed checks results in excluding `r round(nrow(quality_check_failed) / nrow(dur_plot_data) * 100, 1)`% of participants (n = `r nrow(quality_check_failed)`)

# exclude participants

Number of participants before exclusions = `r nrow(filter(surveys_merged_wide))`  
Number of participants after exclusions = `r nrow(filter(surveys_merged_wide, !SID %in% quality_check_notime$SID))`  
Number excluded = `r nrow(quality_check_notime)`

Participants are excluded for:

* Failing the attention check (N = `r nrow(filter(quality_check_notime, n_indicators == 1 & failed_attention == 1))`)  
* Failing the English comprehension check (N = `r nrow(filter(quality_check_notime, n_indicators == 1 & failed_english== 1))`) 
* Having invariance > 3 SDs from the median across people (N = `r nrow(filter(quality_check_notime, n_indicators == 1 & greater_than_3sd_invariance == 1))`)
* More than one of these issues (N = `r nrow(filter(quality_check_notime, n_indicators > 1))`)

```{r}
surveys_clean = surveys_merged %>%
  filter(!SID %in% quality_check_notime$SID) %>% # exclude participants
  select(SID, condition, survey_name, item, value)
```

# summarize condition and survey ns
```{r}
surveys_clean %>%
  group_by(condition) %>%
  select(SID, condition) %>%
  unique() %>%
  summarize(n = n())

surveys_clean %>%
  filter(!is.na(value)) %>%
  group_by(condition, survey_name) %>%
  select(SID, condition, survey_name) %>%
  unique() %>%
  summarize(n = n()) %>%
  spread(condition, n) %>%
  mutate(total = rowSums(.[,2:4], na.rm = TRUE)) %>%
  DT::datatable(filter = "top", rownames = FALSE)
```

# write csvs
```{r}
write.csv(surveys_clean, "../data/study1d_clean_long.csv", row.names = FALSE)
```

