---
title: "Study 4 data cleaning"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(scipen=999)
```

This document provides the code for the analyses reported in:

[Cosme et al. (Preprint) Message self and social relevance is positively related to sharing intentions:
Correlational and causal evidence from six studies]()

This script cleans the raw data from Study 4.

# load packages
```{r}
if (!require(tidyverse)) {
  install.packages('tidyverse')
}
if (!require(readr)) {
  install.packages('readr')
}
if (!require(stringr)) {
  install.packages('stringr')
}
if (!require(reshape2)) {
  install.packages('reshape2')
}
```

# load qualtrics data

```{r}
surveys_raw = read.csv("../../nyt_emotion_study/nytimes+--+emotion+piloting_March+30,+2021_10.47.csv",
                       stringsAsFactors = FALSE)
```

# rename and select relevant variables
```{r}
surveys_rename = surveys_raw %>%
  rename("age" = Q8.1,
         "gender" = Q8.2,
         "lang" = Q8.3,
         "check1" = Q7.2,
         "check2" = Q7.3,
         "check3" = Q7.4,) %>%
  select(Progress, ResponseId, age, gender, lang, contains("check"),
         contains("Q3.5"), contains("Q4.5"),
         contains("Q5.1"), contains("Q6.1")) %>%
  slice(-c(1:2)) %>%
  filter(!as.numeric(Progress) < 98)
```

# failed English comprehension checks
```{r}
failed_check1 = surveys_rename %>%
  filter(!grepl("tim", tolower(check1)))

failed_check2 = surveys_rename %>%
  filter(!grepl("man", tolower(check2)))

failed_check3 = surveys_rename %>%
  filter(!grepl("tim", tolower(check3)))

exclude_english = surveys_rename %>%
  filter(as.numeric(Progress) >= 98) %>%
  filter(ResponseId %in% c(failed_check1$ResponseId,
                            failed_check3$ResponseId,
                            failed_check3$ResponseId,
                            "R_O8dIOfbNbLDeDPb",
                            "R_2D6qZGOLqFv1CoU",
                            "R_O8dIOfbNbLDeDPb",
                            "R_3fdghxUoBSEnu9M",
                            "R_2OYGv6Ctfmx6sB5",
                            "R_wSLwbv5K9a4TOxj",
                            "R_1jvLVYzrQNxBhHU",
                            "R_1rfihdoAdlWS02X"))

```

# exclude participants
Number of participants before exclusions = `r nrow(surveys_rename)`

Number of participants after exclusions = `r nrow(surveys_rename %>% filter(!ResponseId %in% c(exclude_english$ResponseId)))`

Number excluded = `r nrow(exclude_english)`

Participants are excluded for:

* Failing at least one of the English comprehension questions (N = `r nrow(exclude_english)`)

```{r}
surveys_include = surveys_rename %>%
  filter(!ResponseId %in% c(exclude_english$ResponseId))
```

# tidy
```{r}
surveys_tidy = surveys_include %>%
  gather(item, value, contains("Q3.5"), contains("Q4.5"),
         contains("Q5.1"), contains("Q6.1")) %>%
  filter(!value == "") %>%
  mutate(gender = ifelse(grepl("^f|woman", tolower(gender)), "Female", "Male"),
         item = gsub("Q3.5_|Q4.5_|Q5.1_|Q6.1_", "", item),
         item = gsub("_8", "_msg_rel_self", item),
         item = gsub("_9", "_msg_rel_social", item),
         item = gsub("_11", "_msg_share", item)) %>%
  filter(grepl("msg", item)) %>%
  extract(item, c("item", "scale_name"), "X([0-9]+)_(.*)") %>%
  select(-contains("check"), -Progress, -lang)
```

# write csvs
```{r}
write.csv(surveys_tidy, "../data/study4_clean_long.csv", row.names = FALSE)
```
