---
title: "Causal analyses"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, dpi = 150)
options(scipen = 999)
set.seed(65)
```

In these analyses, we test causal relationships between self and social relevance and broad- and narrowcast sharing intentions with data from Study 6.

# define functions
```{r}
# MLM results table function
table_model = function(model_data, eff_size = TRUE) {
  
  results = model_data %>%
    broom.mixed::tidy(conf.int = TRUE) %>%
    filter(effect == "fixed") %>%
    rename("SE" = std.error,
           "t" = statistic,
           "p" = p.value) %>%
    select(-group, -effect) %>%
    mutate_at(vars(-contains("term"), -contains("p.value")), round, 2) %>%
    mutate(term = gsub("article_cond", "", term),
           term = gsub("\\(Intercept\\)", "control", term),
           term = gsub("sharing_type", "sharing type", term),
           term = gsub("msg_rel_self_between", "self-relevance", term),
           term = gsub("msg_rel_social_between", "social relevance", term),
           term = gsub("contentclimate", "content (climate)", term),
           term = gsub("n_c", "word count", term),
           term = gsub(":", " x ", term),
           p = ifelse(p < .001, "< .001",
                      ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
           `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high)) 
  
  if (eff_size == TRUE) {
    eff_size = lme.dscore(model_data, data = study6, type = "lme4") %>%
      rownames_to_column(var = "term") %>%
      mutate(term = gsub("article_cond", "", term),
             term = gsub("article_cond", "", term),
             term = gsub("\\(Intercept\\)", "control", term),
             term = gsub("sharing_type", "sharing type", term),
             term = gsub("msg_rel_self_between", "self-relevance", term),
             term = gsub("msg_rel_social_between", "social relevance", term),
             term = gsub("contentclimate", "content (climate)", term),
             term = gsub(":", " x ", term),
             d = sprintf("%.2f", d)) %>%
      select(term, d)
    
    results %>%
      left_join(., eff_size) %>%
      mutate(d = ifelse(is.na(d), "--", d)) %>%
      select(term, `b [95% CI]`, d, df, t, p) %>%
      kable() %>%
      kableExtra::kable_styling()
    
  } else {
    results %>%
      select(term, `b [95% CI]`, df, t, p) %>%
      kable() %>%
      kableExtra::kable_styling()
  }
}

# Run bayesian mediation model
run_brm_model = function(model_name, model_formula, y_var, data) {
  if (file.exists(sprintf("models/model_%s.RDS", model_name))) {
    assign(get("model_name"), readRDS(sprintf("models/model_%s.RDS", model_name)))
  } else {
    
    assign(get("model_name"),
           brm(
             model_formula,
             data = data,
             cores = 4,
             thin = 4,
             seed = seed,
             control = list(adapt_delta = .99, max_treedepth = 15)
        ))
    
    saveRDS(eval(parse(text = model_name)), sprintf("models/model_%s.RDS", model_name))
    return(eval(parse(text = model_name)))
  }
}

# Get path estimates from bayesian mediation models
create_paths = function(model, x_var, y_var) {
  paths = posterior_samples(model) %>% 
    mutate(a1 = get(sprintf("b_msgrelself_article_cond%s", x_var)),
           a2 = get(sprintf("b_msgrelsocial_article_cond%s", x_var)),
           b1 = get(sprintf("b_%s_msg_rel_self", y_var)),
           b2 = get(sprintf("b_%s_msg_rel_social", y_var)),
           c_prime = get(sprintf("b_%s_article_cond%s", y_var, x_var)),
           a1b1 = a1 * b1,
           a2b2 = a2 * b2,
           c = c_prime + a1b1 + a2b2,
           cor1 = get(sprintf("cor_SID__msgrelself_article_cond%s__%s_msg_rel_self", x_var, y_var)),
           cor2 = get(sprintf("cor_SID__msgrelsocial_article_cond%s__%s_msg_rel_social", x_var, y_var)),
           sd_a1 = get(sprintf("sd_SID__msgrelself_article_cond%s", x_var)),
           sd_b1 = get(sprintf("sd_SID__%s_msg_rel_self", y_var)),
           sd_a2 = get(sprintf("sd_SID__msgrelsocial_article_cond%s", x_var)),
           sd_b2 = get(sprintf("sd_SID__%s_msg_rel_social", y_var)),
           cov_a1b1 = cor1*sd_a1*sd_b1,
           cov_a2b2 = cor2*sd_a2*sd_b2,
           a1b1_cov_a1b1 = a1b1 + cov_a1b1,
           a2b2_cov_a2b2 = a2b2 + cov_a2b2,
           model = x_var,
           outcome = y_var)
  
  return(paths)
}

create_paths_words = function(model, x_var, y_var) {
  y_var = gsub("_", "", y_var)
  paths = posterior_samples(model) %>% 
    mutate(a1 = get(sprintf("b_nc_article_cond%s", x_var)),
           b1 = get(sprintf("b_%s_n_c", y_var)),
           c_prime = get(sprintf("b_%s_article_cond%s", y_var, x_var)),
           a1b1 = a1 * b1,
           c = c_prime + a1b1,
           cor1 = get(sprintf("cor_SID__nc_article_cond%s__%s_n_c", x_var, y_var)),
           sd_a1 = get(sprintf("sd_SID__nc_article_cond%s", x_var)),
           sd_b1 = get(sprintf("sd_SID__%s_n_c", y_var)),
           cov_a1b1 = cor1*sd_a1*sd_b1,
           a1b1_cov_a1b1 = a1b1 + cov_a1b1,
           model = x_var,
           outcome = y_var)
  
  return(paths)
}

get_paths = function(model, x_var, y_var) {
  create_paths(model, x_var, y_var) %>% 
    select(a1:a2b2_cov_a2b2, -contains("sd"), -contains("cor"), -starts_with("cov")) %>% 
    gather(path, value) %>% 
    group_by(path) %>% 
    summarize(median = median(value),
              `Mdn [95% CI]` = sprintf("%.2f [%.2f, %.2f]", median(value), quantile(value, probs = .025), quantile(value, probs = .975))) %>%
    mutate(path = factor(path, levels = c("a1", "b1", "a1b1", "a1b1_cov_a1b1", "a2", "b2", "a2b2", "a2b2_cov_a2b2", "c", "c_prime"))) %>%
    arrange(path) %>%
    select(-median) %>%
    kable() %>%
    kableExtra::kable_styling()
}

get_paths_words = function(model, x_var, y_var) {
  create_paths_words(model, x_var, y_var) %>% 
    select(a1:a1b1_cov_a1b1, -contains("sd"), -contains("cor"), -starts_with("cov")) %>% 
    gather(path, value) %>% 
    group_by(path) %>% 
    summarize(median = median(value),
              `Mdn [95% CI]` = sprintf("%.2f [%.2f, %.2f]", median(value), quantile(value, probs = .025), quantile(value, probs = .975))) %>%
    mutate(path = factor(path, levels = c("a1", "b1", "a1b1", "a1b1_cov_a1b1", "c", "c_prime"))) %>%
    arrange(path) %>%
    select(-median) %>%
    kable() %>%
    kableExtra::kable_styling()
}

percent_mediated = function(model, x_var, y_var) {
  create_paths(model, x_var, y_var) %>% 
    select(a1b1_cov_a1b1, a2b2_cov_a2b2, c) %>% 
    gather(path, value) %>% 
    group_by(path) %>% 
    summarize(median = median(value)) %>%
    select(path, median) %>%
    spread(path, median) %>%
    mutate(self = round((a1b1_cov_a1b1 / c) * 100, 0),
           social = round((a2b2_cov_a2b2 / c) * 100, 0),
           total = self + social) %>%
    select(self, social, total) %>%
    kable(caption = "percent mediated") %>%
    kableExtra::kable_styling()
}

percent_mediated_words = function(model, x_var, y_var) {
  create_paths_words(model, x_var, y_var) %>% 
    select(a1b1_cov_a1b1, c) %>% 
    gather(path, value) %>% 
    group_by(path) %>% 
    summarize(median = median(value)) %>%
    select(path, median) %>%
    spread(path, median) %>%
    mutate(word_count = round((a1b1_cov_a1b1 / c) * 100, 0)) %>%
    select(word_count) %>%
    kable(caption = "percent mediated") %>%
    kableExtra::kable_styling()
}
```

# prep data {.tabset}
First, we load the relevant packages and data, and define the plotting aesthetics.

## load packages
```{r}
if(!require('pacman')) {
	install.packages('pacman')
}

pacman::p_load(tidyverse, knitr, kableExtra, lmerTest, boot, report, brms, tidybayes, ggpubr, tidyText, EMAtools, broom.mixed)
report::cite_packages()
```

## define aesthetics
```{r}
palette_condition = c("#ee9b00", "#bb3e03", "#005f73")
palette_sharing = c("#086E70", "#FFA600")
palette_content = c("#9FC490", "#43BCCD")
palette_relevance = c("#FB590E", "#00667A")

plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 12),
        text = element_text(size = 16, family = "Futura Medium"),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank())
```

## load data
```{r}
study6 = read.csv("../data/study6.csv", stringsAsFactors = FALSE) %>%
  mutate(content = factor(content, levels = c("health", "climate")))

study6_comments = read.csv("../data/study6_comments.csv", stringsAsFactors = FALSE)
```

# condition ns
```{r}
study6 %>%
  select(group, SID) %>%
  unique() %>%
  group_by(group) %>%
  summarize(n = n())
```

# manipulation checks {.tabset}
## self-relevance {.tabset}
Test whether messages in the self condition will be rated as more self-relevant than messages in the control condition.

### run model
```{r}
mod_h1 = lmer(msg_rel_self ~ 1 + article_cond + (1 + article_cond | SID),
              data = study6,
              control = lmerControl(optimizer = "bobyqa"))
summary(mod_h1)
```

### model summary table
```{r}
table_model(mod_h1)
```

## social relevance {.tabset}
Test whether messages in the social condition will be rated as more socially relevant than messages in the control condition.

### run model
```{r}
mod_h2 = lmer(msg_rel_social ~ 1 + article_cond + (1 + article_cond | SID),
              data = study6,
              control = lmerControl(optimizer = "bobyqa"))
summary(mod_h2)
```

### model summary table
```{r}
table_model(mod_h2)
```

# condition effects by sharing type {.tabset}
Test whether messages in the experimental conditions will evoke higher sharing intentions than messages in the control condition, and whether this is moderated by sharing type.

## run model
```{r}
mod_h3_h4 = lmer(msg_share ~ 1 + article_cond*sharing_type + (1 + sharing_type | SID),
              data = study6,
              control = lmerControl(optimizer = "bobyqa"))
summary(mod_h3_h4)
```

## model summary table
```{r}
table_model(mod_h3_h4)
```

# combined plot
This is the plot in Figure 4.

```{r, fig.width=10, fig.height=5}
# generate predicted values
predicted_h1 = ggeffects::ggpredict(mod_h1, c("article_cond")) %>%
              data.frame() %>%
  mutate(model = "self\nrelevance")

predicted_h2 = ggeffects::ggpredict(mod_h2, c("article_cond")) %>%
              data.frame() %>%
  mutate(model = "social\nrelevance")

predicted_h3_h4 = ggeffects::ggpredict(mod_h3_h4, c("article_cond", "sharing_type")) %>%
              data.frame() %>%
  mutate(group = ifelse(group == "0", "broadcast sharing", "narrowcast sharing"))

# manipulation check plot
check = bind_rows(predicted_h1, predicted_h2) %>%
  ggplot(aes(x = model, y = predicted, color = x)) +
    geom_pointrange(aes( ymin = conf.low, ymax = conf.high), position = position_dodge(.5), size = 1) +
    coord_flip() +
    scale_color_manual(name = "", values = palette_condition) +
    scale_y_continuous(limits = c(50, 72)) +
    labs(x = "", y = "\nmean predicted rating") +
    plot_aes +
    theme(legend.position = c(.85, .15))

# causal analysis plot
causal = predicted_h3_h4 %>%
  mutate(group = gsub(" sharing", "", group)) %>%
  ggplot(aes(x = x, y = predicted, color = x)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, alpha = group), position = position_dodge(.5), size = 1) +
  coord_flip() +
  scale_color_manual(name = "", values = palette_condition, guide = "none") +
  scale_alpha_manual(name = "", values = c(1, .5)) +
  labs(x = "", y = "\nmean predicted sharing intention rating") +
  scale_y_continuous(limits = c(40, 60)) +
  plot_aes +
  theme(legend.position = c(.85, .15))

cowplot::plot_grid(check, causal, labels = c("A", "B"))
```

# mediation {.tabset}
Use [Elizabeth Page-Gould's code for estimating indirect effects in multilevel models](http://www.page-gould.com/r/indirectmlm/) to test whether the experimental effects on sharing intentions are mediate through self or social relevance.

## prep data
```{r}
# source functions
source("indirectMLM.R")

# create self condition dataframe
data_med_self = study6 %>%
  filter(group == "self") %>%
  mutate(article_cond = ifelse(article_cond == "self", 1, 0),
         sharing_type = ifelse(sharing_type == 0, "broadcast", "narrowcast"),
         SID = as.character(SID)) %>%
  spread(sharing_type, msg_share) %>%
  select(SID, article_cond, trial, msg_rel_self, broadcast, narrowcast) %>%
  na.omit() %>%
  data.frame()

# create social condition dataframe
data_med_social = study6 %>%
  filter(group == "social") %>%
  mutate(article_cond = ifelse(article_cond == "social", 1, 0),
         sharing_type = ifelse(sharing_type == 0, "broadcast", "narrowcast"),
         SID = as.character(SID)) %>%
  spread(sharing_type, msg_share) %>%
  select(SID, article_cond, trial, msg_rel_social, broadcast, narrowcast) %>%
  na.omit() %>%
  data.frame()
```

## self condition {.tabset}
Test whether there is an indirect effect through self-relevance, such that the self-relevance manipulation will be associated with higher self-relevance ratings, which in turn will be related to stronger a) broadcast and b) narrowcast sharing intentions.

### broadcast intentions
```{r}
y_var = "broadcast"
m_var = "msg_rel_self"
model_name = "mediation_self_broadcast"
data = data_med_self

if (file.exists(sprintf("models/model_%s.RDS", model_name))) {
  assign(get("model_name"), readRDS(sprintf("models/model_%s.RDS", model_name)))
} else {
  assign(get("model_name"), boot(data = data, statistic = indirect.mlm, R = 500,
                                 y = y_var, x = "article_cond", mediator = m_var, group.id = "SID",
                                 between.m = F, uncentered.x = F))
  saveRDS(eval(parse(text = model_name)), sprintf("models/model_%s.RDS", model_name))
}

indirect.mlm.summary(get(model_name))

# percent mediated
sprintf("percent mediated = %s", round(((12.629 * 0.344) / 5.377) * 100, 0))
```

### narrowcast intentions
```{r}
y_var = "narrowcast"
m_var = "msg_rel_self"
model_name = "mediation_self_narrowcast"
data = data_med_self

if (file.exists(sprintf("models/model_%s.RDS", model_name))) {
  assign(get("model_name"), readRDS(sprintf("models/model_%s.RDS", model_name)))
} else {
  assign(get("model_name"), boot(data = data, statistic = indirect.mlm, R = 500,
                                 y = y_var, x = "article_cond", mediator = m_var, group.id = "SID",
                                 between.m = F, uncentered.x = F))
  saveRDS(eval(parse(text = model_name)), sprintf("models/model_%s.RDS", model_name))
}

indirect.mlm.summary(get(model_name))

# percent mediated
sprintf("percent mediated = %s", round(((12.629 * 0.422) / 6.789) * 100, 0))
```

## social condition {.tabset}

Test whether there is an indirect effect through social relevance, such that the social relevance manipulation will be associated with higher social relevance ratings, which in turn will be related to stronger a) broadcast and b) narrowcast sharing intentions.

### broadcast intentions
```{r}
y_var = "broadcast"
m_var = "msg_rel_social"
model_name = "mediation_social_broadcast"
data = data_med_social

if (file.exists(sprintf("models/model_%s.RDS", model_name))) {
  assign(get("model_name"), readRDS(sprintf("models/model_%s.RDS", model_name)))
} else {
  assign(get("model_name"), boot(data = data, statistic = indirect.mlm, R = 500,
                                 y = y_var, x = "article_cond", mediator = m_var, group.id = "SID",
                                 between.m = F, uncentered.x = F))
  saveRDS(eval(parse(text = model_name)), sprintf("models/model_%s.RDS", model_name))
}

indirect.mlm.summary(get(model_name))

# percent mediated
sprintf("percent mediated = %s", round(((8.591 * 0.472) / 3.402) * 100, 0))
```

### narrowcast intentions
```{r}
y_var = "narrowcast"
m_var = "msg_rel_social"
model_name = "mediation_social_narrowcast"
data = data_med_social

if (file.exists(sprintf("models/model_%s.RDS", model_name))) {
  assign(get("model_name"), readRDS(sprintf("models/model_%s.RDS", model_name)))
} else {
  assign(get("model_name"), boot(data = data, statistic = indirect.mlm, R = 500,
                                 y = y_var, x = "article_cond", mediator = m_var, group.id = "SID",
                                 between.m = F, uncentered.x = F))
  saveRDS(eval(parse(text = model_name)), sprintf("models/model_%s.RDS", model_name))
}

indirect.mlm.summary(get(model_name))

# percent mediated
sprintf("percent mediated = %s", round(((8.591 * 0.55) / 7.326) * 100, 0))
```

# post-hoc {.tabset}
These analyses were added in response to feedback from reviewers during peer review.

## moderation by article content {.tabset}
Are the relationships moderated by article content types (health or climate)?

### self-relevance {.tabset}
#### run model
Note: The model allowing both condition and article content type to vary randomly across people did not converge. We therefore used AIC to select the best fitting random effects structure and summarize results from this model

```{r}
mod_h1_1 = lmer(msg_rel_self ~ 1 + article_cond * content + (1 + article_cond | SID),
              data = study6,
              control = lmerControl(optimizer = "bobyqa"))
mod_h1_2 = lmer(msg_rel_self ~ 1 + article_cond * content + (1 + content | SID),
              data = study6,
              control = lmerControl(optimizer = "bobyqa"))
anova(mod_h1_1, mod_h1_2)
summary(mod_h1_2)
```

#### model summary table
```{r}
table_model(mod_h1_2)
```

### social relevance {.tabset}
#### run model
```{r}
mod_h2 = lmer(msg_rel_social ~ 1 + article_cond * content + (1 + article_cond + content | SID),
              data = study6,
              control = lmerControl(optimizer = "bobyqa"))
summary(mod_h2)
```

#### model summary table
```{r}
table_model(mod_h2)
```

### sharing {.tabset}
#### run model
```{r}
mod_h3_h4 = lmer(msg_share ~ 1 + article_cond*sharing_type*content + (1 + sharing_type + content | SID),
              data = study6,
              control = lmerControl(optimizer = "bobyqa"))
summary(mod_h3_h4)
```

#### model summary table
```{r}
table_model(mod_h3_h4)
```

### plot
```{r, fig.width=12, fig.height=5}
# generate predicted values
predicted_h1 = ggeffects::ggpredict(mod_h1_2, c("article_cond", "content")) %>%
              data.frame() %>%
  mutate(model = "self\nrelevance")

predicted_h2 = ggeffects::ggpredict(mod_h2, c("article_cond", "content")) %>%
              data.frame() %>%
  mutate(model = "social\nrelevance")

predicted_h3_h4 = ggeffects::ggpredict(mod_h3_h4, c("article_cond", "sharing_type", "content")) %>%
              data.frame() %>%
  mutate(group = ifelse(group == "0", "broadcast sharing", "narrowcast sharing"))

# manipulation check plot
check = bind_rows(predicted_h1, predicted_h2) %>%
  ggplot(aes(x = x, y = predicted, color = group)) +
  stat_summary(aes(group = group), fun.y = "mean", geom = "line", position = position_dodge(.2), size = 1) + 
  geom_pointrange(aes( ymin = conf.low, ymax = conf.high), position = position_dodge(.2), size = 1) +
  facet_grid(~model) +
  scale_color_manual(name = "", values = palette_content) +
  labs(x = "", y = "mean predicted rating\n") +
  plot_aes +
  theme(legend.position = c(.85, .15))

# causal analysis plot
causal = predicted_h3_h4 %>%
  mutate(group = gsub(" sharing", "", group)) %>%
  ggplot(aes(x = x, y = predicted, color = facet)) + 
  stat_summary(aes(group = facet), fun.y = "mean", geom = "line", position = position_dodge(.2), size = 1) + 
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), position = position_dodge(.2), size = 1) +
  facet_grid(~group) +
  scale_color_manual(name = "", values = palette_content) +
  scale_alpha_manual(name = "", values = c(1, .5)) +
  labs(x = "", y = "mean predicted sharing intention rating\n") +
  scale_y_continuous(limits = c(40, 60)) +
  plot_aes +
  theme(legend.position = c(.85, .15))

cowplot::plot_grid(check, causal, labels = c("A", "B"))
```

## bayesian parallel mediation {.tabset}
To include both self and social relevance as parallel mediators of the relationship between the experimental condition (self, social, or control) and sharing intentions, we estimated four separate models using `{brms}`.

### prep data
```{r}
# create self condition dataframe
data_med_self = study6 %>%
  filter(group == "self") %>%
  mutate(sharing_type = ifelse(sharing_type == 0, "broadcast", "narrowcast")) %>%
  spread(sharing_type, msg_share) %>%
  select(SID, article_cond, trial, msg_rel_social, msg_rel_self, broadcast, narrowcast)

# create social condition dataframe
data_med_social = study6 %>%
  filter(group == "social") %>%
  mutate(sharing_type = ifelse(sharing_type == 0, "broadcast", "narrowcast")) %>%
  spread(sharing_type, msg_share) %>%
  select(SID, article_cond, trial, msg_rel_self, msg_rel_social, broadcast, narrowcast)

# set seed
seed = 6523
```

### self condition {.tabset}
Test whether there is an indirect effect through social relevance, such that the self relevance manipulation will be associated with higher social relevance ratings, which in turn will be related to stronger a) broadcast and b) narrowcast sharing intentions.

#### broadcast intentions
```{r}
x_var = "self"
y_var = "broadcast"
model_name = "mediation_self_broadcast_brm"
data = data_med_self
model_formula = bf(msg_rel_social ~ article_cond + (1 + article_cond |i| SID)) +
  bf(msg_rel_self ~ article_cond + (1 + article_cond |i| SID)) +
  bf(paste0(y_var, " ~ article_cond + msg_rel_social + msg_rel_self + (1 +  msg_rel_social + msg_rel_self |i| SID)")) +
  set_rescor(FALSE)

model_self_broad = run_brm_model(model_name, model_formula, y_var, data)
get_paths(model_self_broad, x_var, y_var)
percent_mediated(model_self_broad, x_var, y_var)
```

#### narrowcast intentions
```{r}
x_var = "self"
y_var = "narrowcast"
model_name = "mediation_self_narrowcast_brm"
data = data_med_self
model_formula = bf(msg_rel_social ~ article_cond + (1 + article_cond |i| SID)) +
  bf(msg_rel_self ~ article_cond + (1 + article_cond |i| SID)) +
  bf(paste0(y_var, " ~ article_cond + msg_rel_social + msg_rel_self + (1 +  msg_rel_social + msg_rel_self |i| SID)")) +
  set_rescor(FALSE)

model_self_narrow = run_brm_model(model_name, model_formula, y_var, data)
get_paths(model_self_narrow, x_var, y_var)
percent_mediated(model_self_narrow, x_var, y_var)
```

### social condition {.tabset}

Test whether there is an indirect effect through social relevance, such that the social relevance manipulation will be associated with higher social relevance ratings, which in turn will be related to stronger a) broadcast and b) narrowcast sharing intentions.

#### broadcast intentions
```{r}
x_var = "social"
y_var = "broadcast"
m_var = "msg_rel_self"
model_name = "mediation_social_broadcast_brm"
data = data_med_social
model_formula = bf(msg_rel_social ~ article_cond + (1 + article_cond |i| SID)) +
  bf(msg_rel_self ~ article_cond + (1 + article_cond |i| SID)) +
  bf(paste0(y_var, " ~ article_cond + msg_rel_social + msg_rel_self + (1 +  msg_rel_social + msg_rel_self |i| SID)")) +
  set_rescor(FALSE)

model_social_broad = run_brm_model(model_name, model_formula, y_var, data)
get_paths(model_social_broad, x_var, y_var)
percent_mediated(model_social_broad, x_var, y_var)
```

#### narrowcast intentions
```{r}
x_var = "social"
y_var = "narrowcast"
m_var = "msg_rel_self"
model_name = "mediation_social_narrowcast_brm"
data = data_med_social
model_formula = bf(msg_rel_social ~ article_cond + (1 + article_cond |i| SID)) +
  bf(msg_rel_self ~ article_cond + (1 + article_cond |i| SID)) +
  bf(paste0(y_var, " ~ article_cond + msg_rel_social + msg_rel_self + (1 +  msg_rel_social + msg_rel_self |i| SID)")) +
  set_rescor(FALSE)

model_social_narrow = run_brm_model(model_name, model_formula, y_var, data)
get_paths(model_social_narrow, x_var, y_var)
percent_mediated(model_social_narrow, x_var, y_var)
```

### combined plot

```{r, fig.width = 9, fig.height = 4.5}
labels = data.frame(model = c("self", "social"),
                    outcome = c("broadcast", "narrowcast"),
                    value = c(1, 1))

create_paths(model_self_broad, "self", "broadcast") %>%
  bind_rows(create_paths(model_self_narrow, "self", "narrowcast")) %>%
  bind_rows(create_paths(model_social_broad, "social", "broadcast")) %>%
  bind_rows(create_paths(model_social_narrow, "social", "narrowcast")) %>%
  select(model, outcome, a1b1_cov_a1b1, a2b2_cov_a2b2) %>% 
  gather(path, value, -model, -outcome) %>%
  mutate(path = ifelse(path == "a1b1_cov_a1b1", "self-relevance", "social relevance")) %>%
  ggplot(aes(x = value, y = "", fill = path)) +
  geom_rect(data = labels,
            aes(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf),
            alpha = .5, fill = "grey") +
  stat_halfeye(alpha = .8) +
  facet_grid(model ~ outcome) +
  scale_y_discrete(expand = c(.1, 0)) +
  scale_fill_manual(values = palette_relevance, name = "mediator") +
  labs(x = "indirect effect", y = "") +
  plot_aes
```


## word count analyses {.tabset}
In these analyses we looked at how depth of processing, operationalized as word count, is related to the outcomes of interest.

### word count by condition
Does word count differ by condition?

#### summarize
```{r}
n_words = study6_comments %>%
  mutate(study = "study 6",
         item = sprintf("%s_%s", content, article_number),
         SID = sprintf("%s_%s", study, SID)) %>%
  group_by(article_cond, SID, item) %>%
  tidytext::unnest_tokens(word, value) %>%
  summarize(n = n()) 

words_ratings = n_words %>%
  left_join(., study6, by = c()) %>%
  ungroup() %>%
  mutate(n_c = n - mean(n, na.rm = TRUE))

n_words %>%
  group_by(article_cond) %>%
  summarize(mean = mean(n, na.rm = TRUE),
            sd = sd(n, na.rm = TRUE),
            min = min(n, na.rm = TRUE),
            max = max(n, na.rm = TRUE)) %>%
  kable(digits = 2) %>%
  kableExtra::kable_styling()
```

#### rsharing
```{r}
mod_words = lmer(n ~ 1 + article_cond + (1 | SID),
              data = n_words,
              control = lmerControl(optimizer = "bobyqa"))

table_model(mod_words, eff_size = FALSE)
```

#### self-relevance
```{r}
mod_words_h1 = lmer(msg_rel_self ~ 1 + n_c + (1 + n_c | SID),
              data = words_ratings,
              control = lmerControl(optimizer = "bobyqa"))

table_model(mod_words_h1, eff_size = FALSE)
```

#### social relevance
```{r}
mod_words_h2 = lmer(msg_rel_social ~ 1 + n_c + (1 + n_c | SID),
              data = words_ratings,
              control = lmerControl(optimizer = "bobyqa"))

table_model(mod_words_h2, eff_size = FALSE)
```

### mediation models {.tabset}
Is the relationship between experimental condition (self, social, or control) and relevance (self or social) mediated by word count?

#### self --> self relevance
```{r}
x_var = "self"
y_var = "msg_rel_self"
model_name = "mediation_self_words_selfrelevance_brm"
data = words_ratings %>%
  filter(group == "self")
model_formula = bf(n_c ~ article_cond + (1 + article_cond |i| SID)) +
  bf(paste0(y_var, " ~ article_cond + n_c + (1 + n_c |i| SID)")) +
  set_rescor(FALSE)

model_self_word = run_brm_model(model_name, model_formula, y_var, data)
get_paths_words(model_self_word, x_var, y_var)
percent_mediated_words(model_self_word, x_var, y_var)
```

#### self --> social relevance
```{r}
x_var = "self"
y_var = "msg_rel_social"
model_name = "mediation_self_words_socialrelevance_brm"
data = words_ratings %>%
  filter(group == "self")
model_formula = bf(n_c ~ article_cond + (1 + article_cond |i| SID)) +
  bf(paste0(y_var, " ~ article_cond + n_c + (1 + n_c |i| SID)")) +
  set_rescor(FALSE)

model_self_word = run_brm_model(model_name, model_formula, y_var, data)
get_paths_words(model_self_word, x_var, y_var)
percent_mediated_words(model_self_word, x_var, y_var)
```

#### social --> social relevance
```{r}
x_var = "social"
y_var = "msg_rel_social"
model_name = "mediation_social_words_socialrelevance_brm"
data = words_ratings %>%
  filter(group == "social")
model_formula = bf(n_c ~ article_cond + (1 + article_cond |i| SID)) +
  bf(paste0(y_var, " ~ article_cond + n_c + (1 + n_c |i| SID)")) +
  set_rescor(FALSE)

model_social_word = run_brm_model(model_name, model_formula, y_var, data)
get_paths_words(model_social_word, x_var, y_var)
percent_mediated_words(model_social_word, x_var, y_var)
```

#### social --> self relevance
```{r}
x_var = "social"
y_var = "msg_rel_self"
model_name = "mediation_social_words_selfrelevance_brm"
data = words_ratings %>%
  filter(group == "social")
model_formula = bf(n_c ~ article_cond + (1 + article_cond |i| SID)) +
  bf(paste0(y_var, " ~ article_cond + n_c + (1 + n_c |i| SID)")) +
  set_rescor(FALSE)

model_social_word = run_brm_model(model_name, model_formula, y_var, data)
get_paths_words(model_social_word, x_var, y_var)
percent_mediated_words(model_social_word, x_var, y_var)
```
