---
title: "Correlational analyses"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(scipen = 999)
```

This document provides the code for the analyses reported in:

[Cosme et al. (Preprint) Message self and social relevance is positively related to sharing intentions:
Correlational and causal evidence from six studies]()


In these analyses, we test correlational associations between self and social relevance and broad- and narrowcast sharing intentions.

# define functions
```{r}
# parameter estimate plotting function for purrr models
plot_model = function(model_data, palette, size = .35) {
  model_data %>%
    mutate(term = gsub("msg_", "", term),
           term = gsub("_", " ", term),
           term = gsub(":", " x ", term),
           term = gsub("rel self", "self", term),
           term = gsub("rel social", "social", term),
           term = gsub(" within", "\nwithin", term),
           term = gsub(" between", "\nbetween", term)) %>%
    ggplot(aes(x = term, y = estimate, color = study)) +
    geom_pointrange(aes( ymin = conf.low, ymax = conf.high), position = position_dodge(.5), size = size) +
    geom_hline(yintercept = 0, color = "grey50", linetype = "dotted") +
    coord_flip() +
    scale_fill_manual(name = "", values = palette) +
    scale_color_manual(name = "", values = palette) +
    labs(x = "", y = "\nstandardized  regression coefficient\n") +
    plot_aes
}

# MLM results table function
table_model = function(model_data) {
  model_data %>%
    rename("SE" = std.error,
           "t" = statistic,
           "p" = p.value) %>%
    select(-group, -effect) %>%
    mutate_at(vars(-contains("term"), -contains("value"), -contains("study")), round, 2) %>%
    mutate(term = gsub("msg_", "", term),
           term = gsub("_", " ", term),
           term = gsub(":", " x ", term),
           term = gsub("rel self", "self", term),
           term = gsub("rel social", "social", term),
           term = gsub("within", "within", term),
           term = gsub("between", "between", term),
           term = gsub("sharing type", "sharing type (narrowcast)", term),
           term = ifelse(grepl("between x ", term), "sharing type (narrowcast) x social relevance between", term),
           p = ifelse(p < .001, "< .001",
                      ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
           `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high)) %>%
    select(study, term, `b [95% CI]`, df, t, p) %>%
    arrange(study) %>%
    kable()  %>%
    kable_styling()
}
```

# prep data {.tabset}
First, we load the relevant packages and data, and define the plotting aesthetics.

## load packages
```{r}
if (!require(tidyverse)) {
  install.packages('tidyverse')
}
if (!require(knitr)) {
  install.packages('knitr')
}
if (!require(kableExtra)) {
  install.packages('kableExtra')
}
if (!require(lmerTest)) {
  install.packages('lmerTest')
}
if (!require(ggpubr)) {
  install.packages('ggpubr')
}

```

## define aesthetics
```{r}
palette = c("#E64626", "#FF9900", "#FFE136", "#E0BF00", "#00A896","#1985A1", "#165F8D", "#5A69AF", "#393993")
palette_sharing = c("#4c5c68", "#B8B3BE")
palette_relevance = c("#A42B13", "#EE6C4D", "#3D5A80", "#98C1D9")

plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 12),
        text = element_text(size = 16, family = "Futura Medium"),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank())
```

## load and merge data
```{r}
# cleaned study data
study1 = read.csv("../data/study1.csv", stringsAsFactors = FALSE)

study2 = read.csv("../data/study2.csv", stringsAsFactors = FALSE)

study3 = read.csv("../data/study3.csv", stringsAsFactors = FALSE)

study4 = read.csv("../data/study4.csv", stringsAsFactors = FALSE)

study5 = read.csv("../data/study5.csv", stringsAsFactors = FALSE)

study6 = read.csv("../data/study6.csv", stringsAsFactors = FALSE) %>%
  select(-article_cond)

# merge dataframes and z-score within study and sharing type
merged = bind_rows(study1, study2, study3, study4, study5, study6) %>%
  group_by(study, sharing_type) %>%
  mutate(msg_share_std = scale(msg_share, scale = TRUE, center = TRUE))
```

# main manuscript analyses
These analyses are reported in the main manuscript.

## descriptives {.tabset}
Generate study descriptives.

```{r}
data_desc = merged %>%
  select(-contains("within"), -contains("between"), -msg_share_std) %>%
  group_by(SID, sharing_type) %>%
  mutate(msg_rel_self_between = mean(msg_rel_self, na.rm = TRUE),
         msg_rel_social_between = mean(msg_rel_social, na.rm = TRUE),
         sharing_type = ifelse(sharing_type == 0, "broadcast sharing intention",
                        ifelse(sharing_type == 1, "narrowcast sharing intention", NA))) %>%
  spread(sharing_type, msg_share)
```

### participant Ns
```{r}
merged %>%
  ungroup() %>%
  select(study, SID) %>%
  unique() %>%
  group_by(study) %>%
  summarize(n = n()) %>%
  kable(format = "pandoc")
```

### means, SDs, and corrlations
Correlations are generated using repeated measures correlations to account for observations nested within participant.

```{r}
# means
means = data_desc %>%
  gather(variable, val, contains("cast"), contains("rel"), -contains("between")) %>%
  group_by(study, variable) %>%
  summarize(`M (SD)` = sprintf("%s (%s)", round(mean(val, na.rm = TRUE), 2), round(sd(val, na.rm = TRUE), 2))) %>%
  mutate(`scale range` = ifelse(grepl("1", study), "1-7",
                  ifelse(grepl("4", study), "0-10", "0-100"))) %>%
  filter(!grepl("NaN", `M (SD)`)) %>%
  select(study, `scale range`, contains("rel"), everything()) %>%
  mutate(variable = ifelse(variable == "msg_rel_self", "self-relevance",
                    ifelse(variable == "msg_rel_social", "social relevance", variable)))

# correlations with broadcasting intentions
corrs_broad = data_desc %>%
  nest(-c(study)) %>%
  mutate(self_social = map(data, ~ rmcorr::rmcorr(as.factor(SID), msg_rel_self, msg_rel_social, .)),
         self_broad = map(data, ~ rmcorr::rmcorr(as.factor(SID), msg_rel_self, `broadcast sharing intention`, .)),
         social_broad = map(data, ~ rmcorr::rmcorr(as.factor(SID), msg_rel_social, `broadcast sharing intention`, .))) %>%
  select(-data)

# correlations with narrowcasting intentions
corrs_narrow = data_desc %>%
  nest(-study) %>%
  filter(grepl("3|5|6", study)) %>%
  mutate(self_narrow = map(data, ~ rmcorr::rmcorr(as.factor(SID), msg_rel_self, `narrowcast sharing intention`, .)),
         social_narrow = map(data, ~ rmcorr::rmcorr(as.factor(SID), msg_rel_social, `narrowcast sharing intention`, .)),
         broad_narrow = map(data, ~ rmcorr::rmcorr(as.factor(SID), `broadcast sharing intention`, `narrowcast sharing intention`, .))) %>%
  select(-data)

# broadcasting table
broad = corrs_broad %>%
  gather(test, model, contains("self"), contains("social")) %>%
  group_by(study, test) %>%
  filter(!is.null(model)) %>%
  mutate(r = sprintf("%.2f [%.2f, %.2f]", model[[1]][[1]], model[[1]][[4]][1], model[[1]][[4]][2]),
         df = model[[1]][[2]],
         p = round(model[[1]][[3]], 3),
         p = ifelse(p == 0, "< .001", as.character(p))) %>%
  ungroup() %>%
  select(study, test, r) %>%
  extract(test, c("var1", "var2"), "(.*)_(.*)") %>%
  spread(var2, r) %>%
  select(study, var1, everything())

# narrowcasting table
narrow = corrs_narrow %>%
  gather(test, model, contains("self"), contains("social"), contains("broad")) %>%
  group_by(study, test) %>%
  filter(!is.null(model)) %>%
  mutate(r = sprintf("%.2f [%.2f, %.2f]", model[[1]][[1]], model[[1]][[4]][1], model[[1]][[4]][2]),
         df = model[[1]][[2]],
         p = round(model[[1]][[3]], 3),
         p = ifelse(p == 0, "< .001", as.character(p))) %>%
  ungroup() %>%
  select(study, test, r) %>%
  extract(test, c("var1", "var2"), "(.*)_(.*)") %>%
  spread(var2, r) %>%
  select(study, var1, everything())

# combined table
corrs = broad %>%
  bind_rows(., narrow)  %>%
  group_by(study, var1) %>%
  fill(everything(), .direction = "updown") %>%
  unique() %>%
  mutate_if(is.character, ~ ifelse(is.na(.), "--", .)) %>%
  mutate(var1 = ifelse(var1 == "social", "social relevance",
                ifelse(var1 == "self", "self-relevance",
                ifelse(var1 == "broad", "broadcast sharing intention", "narrowcast sharing intention"))),
         `self-relevance` = "--") %>%
  rename("variable" = var1,
         "broadcast sharing intention" = broad,
         "narrowcast sharing intention" = narrow,
         "social relevance" = social) %>%
  select(study, variable, `broadcast sharing intention`, `self-relevance`, `social relevance`, `narrowcast sharing intention`)

# merge descriptors and correlations to generate manuscript table
means %>%
  left_join(., corrs)%>%
  mutate_if(is.character, ~ ifelse(is.na(.), "--", .)) %>%
  kable(format = "pandoc")
```

### messages
```{r}
merged %>%
  ungroup() %>%
  select(item) %>%
  unique() %>%
  summarize(n = n()) %>%
  kable(format = "pandoc")
```

## mega-analysis {.tabset}
### run model
```{r}
model_compare = lmerTest::lmer(msg_share_std ~ 0 + msg_rel_self_between*sharing_type +
                                 msg_rel_self_within*sharing_type +
                                 msg_rel_social_between*sharing_type +
                                 msg_rel_social_within*sharing_type +
                                 (1 + msg_rel_self_within + msg_rel_social_within | SID) +
                                 (1 + msg_rel_self_within + msg_rel_social_within | item),
                               data = merged,
                       control = lmerControl(optimizer = "bobyqa"))

summary(model_compare)
```

### print variance inflation factors
```{r}
car::vif(model_compare)
```

### plot
This is the plot in Figure 1.

```{r, fig.width=10, fig.height=6}
predicted = ggeffects::ggpredict(model_compare, c("msg_rel_self_between [-3:3]", "sharing_type")) %>%
  data.frame() %>%
  mutate(type = "self_between") %>%
  bind_rows(ggeffects::ggpredict(model_compare, c("msg_rel_self_within [-3:3]", "sharing_type")) %>%
              data.frame() %>%
              mutate(type = "self_within")) %>%
  bind_rows(ggeffects::ggpredict(model_compare, c("msg_rel_social_between [-3:3]", "sharing_type")) %>%
              data.frame() %>%
              mutate(type = "social_between")) %>%
  bind_rows(ggeffects::ggpredict(model_compare, c("msg_rel_social_within [-3:3]", "sharing_type")) %>%
              data.frame() %>%
              mutate(type = "social_within"))

points = merged %>%
  select(-group) %>%
  rename("group" = sharing_type,
         "predicted" = msg_share_std) %>%
  select(study, SID, group, predicted, contains("within"), contains("between")) %>%
  gather(type, x, contains("msg")) %>%
  mutate(type = gsub("msg_rel_", "", type),
         group = ifelse(group == 0, "broadcast", "narrowcast")) %>%
  extract(type, c("variable", "type"), "(.*)_(.*)") %>%
  filter(x < 3 & x > -3)

predicted %>%
  mutate(group = ifelse(group == 0, "broadcast", "narrowcast")) %>%
  extract(type, c("variable", "type"), "(.*)_(.*)") %>%
  ggplot(aes(x, predicted, color = group, fill = group, linetype = type)) +
  geom_point(data = points, aes(x, predicted), alpha = .02, size = .25) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2, color = NA) +
  geom_line(size = 1) +
  facet_grid(~variable) +
  scale_color_manual(name = "", values = palette_sharing) +
  scale_fill_manual(name = "", values = palette_sharing) +
  scale_linetype_manual(name = "", values = c("solid", "dotted")) +
  guides(linetype = guide_legend(override.aes = list(fill = NA))) +
  labs(x = "\nstandardized relevance rating", y = "predicted standardized sharing intention rating\n") +
  plot_aes  +
  theme(legend.position = "top")
```

### model summary table
```{r, fig.width=10, fig.height=4.5}
model_compare %>%
  broom.mixed::tidy(conf.int = TRUE) %>%
  filter(effect == "fixed") %>%
  rename("SE" = std.error,
         "t" = statistic,
         "p" = p.value) %>%
  select(-group, -effect) %>%
  mutate_at(vars(-contains("term"), -contains("p.value")), round, 2) %>%
  mutate(term = gsub(":", " x ", term),
         term = gsub("msg_", "", term),
         term = gsub("_", " ", term),
         term = gsub("within", "within", term),
         term = gsub("between", "between", term),
         term = gsub("rel self", "Self", term),
         term = gsub("rel social", "Social", term),
         term = gsub("sharing type", "Sharing type", term),
         term = gsub("Sharing type x (.*)", "\\1 x Sharing type", term),
         p = ifelse(p < .001, "< .001",
                    ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
         `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high)) %>%
  select(term, `b [95% CI]`, df, t, p) %>%
  kable()  %>%
  kable_styling()
```

# supplementary material analyses
These analyses are reported in the supplementary material. Each model is estimated separately for each study rather than being combined as in the mega-analysis.

## separate models {.tabset}
Estimate models with self and social relevance separately.

### self relevance {.tabset}
#### run models
```{r, fig.width=6, fig.height=6}
# define model function
fit_mod = function(data){
  mod = lmerTest::lmer(msg_share_std ~ 0 + msg_rel_self_between + msg_rel_self_within +
                         (1 + msg_rel_self_within | SID) +
                         (1 | item), data = data,
                       control = lmerControl(optimizer = "bobyqa"))
  return(mod)
}

# estimate models
model_lmer_self = merged %>%
  mutate(study = ifelse(sharing_type == 0, sprintf("%s\n%s", study, "broadcast"), sprintf("%s\n%s", study, "narrowcast"))) %>%
  group_by(study) %>%
  nest() %>%
  mutate(test = map(data, fit_mod))

# tidy models
model_data_self = model_lmer_self %>% 
  mutate(tidied = map(test, broom.mixed::tidy, conf.int = TRUE)) %>%
  select(-data, -test) %>%
  unnest() %>%
  filter(effect == "fixed" & grepl("msg", term)) %>%
  rename("term" = term) %>%
  ungroup()
```

#### model summary table
```{r}
table_model(model_data_self)
```

### social relevance {.tabset}
#### run model
This plot is supplementary and not reported in the manuscript.
```{r, fig.width=6, fig.height=6}
# define model function
fit_mod = function(data){
  mod = lmerTest::lmer(msg_share_std ~ 0 + msg_rel_social_between + msg_rel_social_within +
                         (1 + msg_rel_social_within | SID) +
                         (1 | item), data = data,
                       control = lmerControl(optimizer = "bobyqa"))

  return(mod)
}

# estimate models
model_lmer_social = merged  %>%
  mutate(study = ifelse(sharing_type == 0, sprintf("%s\n%s", study, "broadcast"), sprintf("%s\n%s", study, "narrowcast"))) %>%
  group_by(study) %>%
  nest() %>%
  mutate(test = map(data, fit_mod))

# tidy models
model_data_social = model_lmer_social %>% 
  mutate(tidied = map(test, broom.mixed::tidy, conf.int = TRUE)) %>%
  select(-data, -test) %>%
  unnest() %>%
  filter(effect == "fixed" & grepl("msg", term)) %>%
  ungroup()
```

#### model summary table
```{r}
table_model(model_data_social)
```

## combined models{.tabset}
Estimate models with self and social relevance in the same model.

### run models
```{r, fig.width=6, fig.height=6}
fit_mod = function(data){
  mod = lmerTest::lmer(msg_share_std ~ 0 + msg_rel_self_between + msg_rel_self_within +
                         msg_rel_social_between + msg_rel_social_within +
                         (1 + msg_rel_self_within + msg_rel_social_within | SID) +
                         (1 | item), data = data,
                       control = lmerControl(optimizer = "bobyqa"))
  return(mod)
}

model_lmer = merged  %>%
  mutate(study = ifelse(sharing_type == 0, sprintf("%s\n%s", study, "broadcast"), sprintf("%s\n%s", study, "narrowcast"))) %>%
  group_by(study) %>%
  nest() %>%
  mutate(test = map(data, fit_mod))

model_data = model_lmer %>% 
  mutate(tidied = map(test, broom.mixed::tidy, conf.int = TRUE)) %>%
  select(-data, -test) %>%
  unnest() %>%
  filter(effect == "fixed" & grepl("msg", term)) %>%
  ungroup()
```

### model summary table
```{r}
table_model(model_data)
```

## separate and combined plot
This plot is reported in supplementary material Figure S6.

```{r, fig.width=12, fig.height=7}
self_social = bind_rows(model_data_self, model_data_social) %>%
  plot_model(., palette) +
  annotate("label", x = Inf, y = -Inf, hjust = -.05, vjust = 1,
           label = " separated relevance models", family = "Futura Medium", size = 6,
           fill = "white", label.size = NA) +
  scale_y_continuous(limits = c(-.25, 1), breaks = seq(-.25, 1, .25)) +
  guides(colour = guide_legend(nrow = 1)) +
  theme(legend.position = "none",
        legend.text = element_text(size = 12),
        text = element_text(size = 18, family = "Futura Medium"))

combined = plot_model(model_data, palette) +
  annotate("label", x = Inf, y = -Inf, hjust = -.05, vjust = 1, label = "combined relevance models",
           family = "Futura Medium", size = 6, fill = "white", label.size = NA) +
  scale_y_continuous(limits = c(-.25, 1), breaks = seq(-.25, 1, .25)) +
  theme(legend.position = "none",
        legend.text = element_text(size = 12),
        text = element_text(size = 18, family = "Futura Medium"))

ggarrange(self_social, combined, ncol = 2, common.legend = TRUE, legend = "top", labels = c("A", "B"))
```

## sharing type {.tabset}
Estimate models including interactions with sharing type.

### run models
```{r}
fit_mod = function(data){
  mod = lmerTest::lmer(msg_share_std ~ 0 + msg_rel_social_between*sharing_type +
                         msg_rel_social_within*sharing_type +
                         msg_rel_self_between*sharing_type +
                         msg_rel_self_within*sharing_type +
                         (1 + msg_rel_self_within + msg_rel_social_within | SID) +
                         (1 | item), data = data,
                       control = lmerControl(optimizer = "bobyqa"))
  return(mod)
}

model_lmer = merged  %>%
  filter(grepl("3|5|6", study)) %>%
  group_by(study) %>%
  nest() %>%
  mutate(test = map(data, fit_mod))


model_data = model_lmer %>% 
  mutate(tidied = map(test, broom.mixed::tidy, conf.int = TRUE)) %>%
  select(-data, -test) %>%
  unnest() %>%
  filter(effect == "fixed" & grepl("msg|sharing", term)) %>%
  ungroup()
```

### model summary table
```{r}
table_model(model_data)
```
