---
title: "Demographics"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(scipen = 999)
```

This document provides the code for the analyses reported in:

[Cosme et al. (Preprint) Message self and social relevance is positively related to sharing intentions:
Correlational and causal evidence from six studies]()


This code summarizes demographic information across studies and for each study separately. 

# prep data {.tabset}
## load packages
```{r}
if (!require(tidyverse)) {
  install.packages('tidyverse')
}
if (!require(kableExtra)) {
  install.packages('kableExtra')
}
if (!require(usmap)) {
  install.packages('usmap')
}
```

## define aesthetics
```{r}
palette = c("#3B9AB2", "#EBCC2A", "#F21A00")
```

## load and merge data
```{r}
# demographic data
study1 = read.csv("../data/study1_demo.csv", stringsAsFactors = FALSE)

study2 = read.csv("../data/study2_demo.csv", stringsAsFactors = FALSE)

study3 = read.csv("../data/study3_demo.csv", stringsAsFactors = FALSE)

study4 = read.csv("../data/study4_demo.csv", stringsAsFactors = FALSE)

study5 = read.csv("../data/study5_demo.csv", stringsAsFactors = FALSE)

study6 = read.csv("../data/study6_demo.csv", stringsAsFactors = FALSE)

# merge
merged = bind_rows(study1, study2, study3, study4, study5 ,study6)

# tidy
demo = merged %>%
  mutate(value = ifelse(value == "Would rather not say", "Prefer not to say", value),
         value = ifelse(is.na(value), "Not reported", value)) %>%
  group_by(study, item, value) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  filter(!item %in% c("gender_4_TEXT", "race_self")) %>%
  rename(" " = item)
```

# geographic distribution {.tabset}
## by study {.tabset}
### study 1
```{r}
states = merged %>%
  filter(grepl("state", item)) %>%
  spread(item, value) %>%
  filter(study == "study 1") %>%
  group_by(state) %>%
  summarize(n = n())

states %>%
  usmap::plot_usmap(data = ., values = "n", color = "grey50") +
  scale_fill_gradient2(low = palette[1], mid = palette[2], midpoint = max(states$n) / 2, high = palette[3],
                       name = "", na.value = NA, limits = c(0, max(states$n)), breaks = seq(0, max(states$n), 50)) +
  theme(text = element_text(size = 12, family = "Futura Medium"),
        legend.position = "right")
```

### study 5
```{r}
states = merged %>%
  filter(grepl("state", item)) %>%
  spread(item, value) %>%
  filter(study == "study 5") %>%
  group_by(state) %>%
  summarize(n = n())

states %>%
  usmap::plot_usmap(data = ., values = "n", color = "grey50") +
  scale_fill_gradient2(low = palette[1], mid = palette[2], midpoint = max(states$n) / 2, high = palette[3],
                       name = "", na.value = NA, limits = c(0, max(states$n)), breaks = seq(0, max(states$n), 10)) +
  theme(text = element_text(size = 12, family = "Futura Medium"),
        legend.position = "right")
```

### study 6
```{r}
states = merged %>%
  filter(grepl("state", item)) %>%
  spread(item, value) %>%
  filter(study == "study 6") %>%
  group_by(state) %>%
  summarize(n = n())

states %>%
  usmap::plot_usmap(data = ., values = "n", color = "grey50") +
  scale_fill_gradient2(low = palette[1], mid = palette[2], midpoint = max(states$n) / 2, high = palette[3],
                       name = "", na.value = NA, limits = c(0, max(states$n)), breaks = seq(0, max(states$n), 10)) +
  theme(text = element_text(size = 12, family = "Futura Medium"),
        legend.position = "right")
```

## combined
```{r}
states = merged %>%
  filter(grepl("state", item)) %>%
  spread(item, value) %>%
  group_by(state) %>%
  summarize(n = n())

states %>%
  usmap::plot_usmap(data = ., values = "n", color = "grey50") +
  scale_fill_gradient2(low = palette[1], mid = palette[2], midpoint = max(states$n) / 2, high = palette[3],
                       name = "", na.value = NA, limits = c(0, max(states$n)), breaks = seq(0, max(states$n), 50)) +
  theme(text = element_text(size = 12, family = "Futura Medium"),
        legend.position = "right")
```

# age {.tabset}
## by study
```{r}
merged %>%
  filter(item == "age") %>%
  mutate(value = as.numeric(value)) %>%
  group_by(study) %>%
  summarize(`age range` = sprintf("%s - %s", min(value, na.rm = TRUE), max(value, na.rm = TRUE)),
            `mean age` = mean(value, na.rm = TRUE),
            `sd age` = sd(value, na.rm = TRUE)) %>%
  kable(digits = 1) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

## combined
```{r}
merged %>%
  filter(item == "age") %>%
  mutate(value = as.numeric(value)) %>%
  summarize(`age range` = sprintf("%s - %s", min(value, na.rm = TRUE), max(value, na.rm = TRUE)),
            `mean age` = mean(value, na.rm = TRUE),
            `sd age` = sd(value, na.rm = TRUE)) %>%
  kable(digits = 1) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

## student year
```{r}
demo %>%
  filter(` ` == "student_grade") %>%
  group_by(study) %>%
  mutate(total = sum(n),
         percent = sprintf("%.1f%s", (n / total) * 100, "%"),
         value = ifelse(is.na(value), "Not reported", value)) %>%
  select(-n, -total, -` `) %>%
  spread(study, percent) %>%
  mutate(value = factor(value, c("First year", "Second year", "Third year",
                                 "Fourth year", "Fifth year or higher"))) %>%
  arrange(value) %>%
  kable(digits = 1) %>%
    kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

# gender {.tabset}
## by study
```{r}
demo %>%
  filter(` ` == "gender") %>%
  group_by(study) %>%
  mutate(total = sum(n),
         percent = sprintf("%.1f%s", (n / total) * 100, "%"),
         value = ifelse(is.na(value), "Not reported", value)) %>%
  select(-n, -total, -` `) %>%
  spread(study, percent) %>%
  mutate_if(is.character, funs(ifelse(is.na(.), "—", .))) %>%
  kable(digits = 1) %>%
    kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

## combined
```{r}
demo %>%
  filter(` ` == "gender") %>%
  group_by(value) %>%
  summarize(n = sum(n)) %>%
  mutate(total = sum(n),
         percent = sprintf("%.1f%s", (n / total) * 100, "%"),
         value = ifelse(is.na(value), "Not reported", value)) %>%
  select(-n, -total) %>%
  mutate_if(is.character, funs(ifelse(is.na(.), "—", .))) %>%
  kable(digits = 1) %>%
    kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

# race and ethnicity {.tabset}
## by study
```{r}
hispanic_latinx = demo %>%
  filter(` ` == "Hispanic or Latinx") %>%
  group_by(study) %>%
  mutate(total = sum(n),
         percent = sprintf("%.1f%s", (n / total) * 100, "%")) %>%
  select(-n, -total) %>%
  spread(value, percent) %>%
  select(study, Yes) %>%
  rename("percent" = Yes) %>%
  mutate(`race / ethnicity` = "Hispanic or Latinx")

demo %>%
  filter(` ` == "race") %>%
  filter(!value %in% c("Hispanic", "Latino")) %>% #counted already in the hispanic_latinx item
  group_by(study) %>%
  mutate(total = sum(n),
         percent = sprintf("%.1f%s", (n / total) * 100, "%"),
         value = ifelse(is.na(value), "Not reported", value)) %>%
  select(study, value, percent) %>%
  rename("race / ethnicity" = value) %>%
  bind_rows(., hispanic_latinx) %>%
  arrange(`race / ethnicity`) %>%
  spread(study, percent) %>%
  mutate_if(is.character, funs(ifelse(is.na(.), "—", .))) %>%
  kable(digits = 1) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

## combined
```{r}
hispanic_latinx = demo %>%
  filter(` ` == "Hispanic or Latinx") %>%
  group_by(value) %>%
  summarize(n = sum(n)) %>%
  mutate(total = sum(n),
         percent = sprintf("%.1f%s", (n / total) * 100, "%")) %>%
  select(-n, -total) %>%
  spread(value, percent) %>%
  select(Yes) %>%
  rename("percent" = Yes) %>%
  mutate(`race / ethnicity` = "Hispanic or Latinx")

demo %>%
  filter(` ` == "race") %>%
  filter(!value %in% c("Hispanic", "Latino")) %>% #counted already in the hispanic_latinx item
  group_by(value) %>%
  summarize(n = sum(n)) %>%
  ungroup() %>%
  mutate(total = sum(n),
         percent = sprintf("%.1f%s", (n / total) * 100, "%"),
         value = ifelse(is.na(value), "Not reported", value)) %>%
  select(value, percent) %>%
  rename("race / ethnicity" = value) %>%
  bind_rows(., hispanic_latinx) %>%
  arrange(`race / ethnicity`) %>%
  mutate_if(is.character, funs(ifelse(is.na(.), "—", .))) %>%
  kable(digits = 1) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

# education {.tabset}
## by study
```{r}
demo %>%
  filter(` ` == "highest degree completed") %>%
  group_by(study) %>%
  mutate(total = sum(n),
         percent = sprintf("%.1f%s", (n / total) * 100, "%")) %>%
  mutate(value = factor(value, levels = c("Less than high school", "High school graduate (diploma)", "High school graduate (GED)", 
                                          "Some college (1-4 years, no degree)", "Associate's degree (including occupational or academic degrees)",
                                          "Bachelor's degree (BA, BS, etc)", "Master's degree (MA, MS, MENG, MSW, etc)",
                                          "Professional school degree (MD, DDC, JD, etc)", "Doctorate degree (PhD, EdD, etc)"))) %>%
  arrange(value) %>%
  select(study, value, percent) %>%
  rename("highest degree completed" = value) %>%
  spread(study, percent) %>%
  mutate_if(is.character, funs(ifelse(is.na(.), "—", .))) %>%
  kable(digits = 1) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

## combined
```{r}
demo %>%
  filter(` ` == "highest degree completed") %>%
  group_by(value) %>%
  summarize(n = sum(n)) %>%
  mutate(total = sum(n),
         percent = sprintf("%.1f%s", (n / total) * 100, "%")) %>%
  mutate(value = factor(value, levels = c("Less than high school", "High school graduate (diploma)", "High school graduate (GED)", 
                                          "Some college (1-4 years, no degree)", "Associate's degree (including occupational or academic degrees)",
                                          "Bachelor's degree (BA, BS, etc)", "Master's degree (MA, MS, MENG, MSW, etc)",
                                          "Professional school degree (MD, DDC, JD, etc)", "Doctorate degree (PhD, EdD, etc)"))) %>%
  arrange(value) %>%
  select(value, percent) %>%
  rename("highest degree completed" = value) %>%
  mutate_if(is.character, funs(ifelse(is.na(.), "—", .))) %>%
  kable(digits = 1) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

# SES {.tabset}
## by study
```{r}
demo %>%
  filter(` ` == "household income") %>%
  group_by(study) %>%
  mutate(total = sum(n),
         percent = sprintf("%.1f%s", (n / total) * 100, "%")) %>%
  mutate(value = ifelse(is.na(value), "Not reported", value),
         value = factor(value, levels = c("Less than $5,000", "$5,000 through $11,999", "$12,000 through $15,999", "$16,000 through $24,999", 
                                          "$25,000 through $34,999", "$35,000 through $49,999", "$50,000 through $74,999", "$75,000 through $99,999",
                                          "$100,000 and greater", "Not reported"))) %>%
  arrange(value) %>%
  select(study, value, percent) %>%
  rename("household income" = value) %>%
  spread(study, percent) %>%
  mutate_if(is.character, funs(ifelse(is.na(.), "—", .))) %>%
  kable(digits = 1) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

## combined
```{r}
demo %>%
  filter(` ` == "household income") %>%
  group_by(value) %>%
  summarize(n = sum(n)) %>%
  mutate(total = sum(n),
         percent = sprintf("%.1f%s", (n / total) * 100, "%")) %>%
  mutate(value = ifelse(is.na(value), "Not reported", value),
         value = factor(value, levels = c("Less than $5,000", "$5,000 through $11,999", "$12,000 through $15,999", "$16,000 through $24,999", 
                                          "$25,000 through $34,999", "$35,000 through $49,999", "$50,000 through $74,999", "$75,000 through $99,999",
                                          "$100,000 and greater", "Not reported"))) %>%
  arrange(value) %>%
  select(value, percent) %>%
  rename("household income" = value) %>%
  mutate_if(is.character, funs(ifelse(is.na(.), "—", .))) %>%
  kable(digits = 1) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
