---
title: "Downsampled analyses"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(scipen = 999)
```

In these analyses, we test correlational associations between self and social relevance and broad- and narrowcast sharing intentions in a subset of data in which the correlations between self and social relevance are lower.

# prep data {.tabset}
First, we load the relevant packages and data, and define the plotting aesthetics.

## load packages
```{r}
if (!require(tidyverse)) {
  install.packages('tidyverse')
}
if (!require(knitr)) {
  install.packages('knitr')
}
if (!require(kableExtra)) {
  install.packages('kableExtra')
}
if (!require(lmerTest)) {
  install.packages('lmerTest')
}
if (!require(report)) {
  install.packages('report')
}
report::cite_packages()
```

## define aesthetics
```{r}
palette = c("#001219", "#005F73", "#0A9396", "#94D2BD", "#E9D8A6", "#EE9B00", "#CA6702", "#BB3E03", "#AE2012")
palette_sharing = c("#0a9396", "#EE9B00")
palette_study = c("#001219", "#005F73", "#94D2BD", "#E9D8A6", "#EE9B00", "#AE2012")

plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 12),
        text = element_text(size = 16, family = "Futura Medium"),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank())
```

## load and merge data
```{r}
# cleaned study data
study1 = read.csv("../data/study1.csv", stringsAsFactors = FALSE)

study2 = read.csv("../data/study2.csv", stringsAsFactors = FALSE)

study3 = read.csv("../data/study3.csv", stringsAsFactors = FALSE)

study4 = read.csv("../data/study4.csv", stringsAsFactors = FALSE)

study5 = read.csv("../data/study5.csv", stringsAsFactors = FALSE)

study6 = read.csv("../data/study6.csv", stringsAsFactors = FALSE) %>%
  select(-article_cond)

# merge dataframes and z-score within study and sharing type
merged = bind_rows(study1, study2, study3, study4, study5, study6) %>%
  group_by(study, sharing_type) %>%
  mutate(msg_share_std = scale(msg_share, scale = TRUE, center = TRUE))
```

# message-level {.tabset}
In these analyses, select a subset of messages that have correlations between self and social relevance < .7.

## correlations {.tabset}
### descriptives {.tabset}
Describe the correlations between self and social relevance by study and content type.

#### across content
```{r}
cors_spread = merged %>%
  ungroup() %>%
  select(study, item, msg_rel_self, msg_rel_social) %>%
  unique()

cors = cors_spread %>%
  nest(-c(study, item)) %>%
  mutate(test = map(data, possibly(~ cor.test(.$msg_rel_self, .$msg_rel_social), otherwise = NULL))) %>%
  filter(!test == "NULL") %>%
  mutate(coefs = map(test,
                     broom::tidy,
                     conf.int = TRUE,
                     conf.level = .95)) %>% 
  unnest(coefs, .drop = TRUE) %>%
  mutate_if(is.numeric, round, 2)

cors %>%
  group_by(study) %>%
  summarize(`mean correlation` = mean(estimate, na.rm = TRUE),
            `sd correlation` = sd(estimate, na.rm = TRUE),
            min = min(estimate, na.rm = TRUE),
            max = max(estimate, na.rm = TRUE)) %>%
  mutate(`range correlation` = sprintf("%.2f, %.2f", min, max)) %>%
  select(-min, -max) %>%
  kable(digits = 2) %>%
  kableExtra::kable_styling()
```

#### by content
```{r}
message_content = merged %>%
  ungroup() %>%
  select(study, item, content) %>%
  unique()

cors %>%
  left_join(., message_content) %>%
  group_by(study, content) %>%
  summarize(`mean correlation` = mean(estimate, na.rm = TRUE),
            `sd correlation` = sd(estimate, na.rm = TRUE),
            min = min(estimate, na.rm = TRUE),
            max = max(estimate, na.rm = TRUE)) %>%
  mutate(`range correlation` = sprintf("%.2f, %.2f", min, max)) %>%
  select(-min, -max) %>%
  kable(digits = 2) %>%
  kableExtra::kable_styling()
```

### plot
This plot is reported in supplementary material Figure S1.

```{r, fig.width=8, fig.height=5}
cors %>%
  arrange(study, item) %>%
  mutate(item = row_number(),
         V1 = sprintf("self_%s", row_number()),
         V2 = sprintf("social_%s", row_number())) %>%
  ggplot(aes(item, estimate, color = study)) +
  geom_point() +
  geom_hline(yintercept = .7) +
  scale_color_manual(values = palette_study) +
  labs(x = "\nmessage number", y = "correlation between\nself and social relevance\n") +
  plot_aes +
  theme(legend.text = element_text(size = 11))
```

### number of messages per study with < .7 correlation
```{r}
data_lower_cors = cors %>%
  filter(estimate < .7)

total_n = merged %>%
  ungroup() %>%
  select(study, item) %>%
  unique() %>%
  group_by(study) %>%
  summarize(`total n` = n())

data_lower_cors %>%
  group_by(study) %>%
  summarize(n = n()) %>%
  left_join(., total_n) %>%
  mutate(percent = (n / `total n`) * 100) %>%
  kable(digits = 2) %>%
  kableExtra::kable_styling()
```

## downsampled mega-analysis {.tabset}
Estimate the mega-analysis model in the downsampled dataset.

### run model
```{r}
data_downsample = merged %>%
  filter(item %in% data_lower_cors$item)

model = lmerTest::lmer(msg_share_std ~ 0 + msg_rel_self_between*sharing_type +
                                 msg_rel_self_within*sharing_type +
                                 msg_rel_social_between*sharing_type +
                                 msg_rel_social_within*sharing_type +
                                 (1 + msg_rel_self_within + msg_rel_social_within | SID) +
                                 (1 + msg_rel_self_within + msg_rel_social_within | item),
                               data = data_downsample,
                       control = lmerControl(optimizer = "bobyqa"))

summary(model)
```

### print variance inflation factors
```{r}
car::vif(model)
```

### plot
This plot is reported in supplementary material Figure S2.

```{r, fig.width=10, fig.height=6}
predicted = ggeffects::ggpredict(model, c("msg_rel_self_between [-3:3]", "sharing_type")) %>%
  data.frame() %>%
  mutate(type = "self_between") %>%
  bind_rows(ggeffects::ggpredict(model, c("msg_rel_self_within [-3:3]", "sharing_type")) %>%
              data.frame() %>%
              mutate(type = "self_within")) %>%
  bind_rows(ggeffects::ggpredict(model, c("msg_rel_social_between [-3:3]", "sharing_type")) %>%
              data.frame() %>%
              mutate(type = "social_between")) %>%
  bind_rows(ggeffects::ggpredict(model, c("msg_rel_social_within [-3:3]", "sharing_type")) %>%
              data.frame() %>%
              mutate(type = "social_within"))

points = data_downsample %>%
  select(-group) %>%
  rename("group" = sharing_type,
         "predicted" = msg_share_std) %>%
  select(study, SID, group, predicted, contains("within"), contains("between")) %>%
  gather(type, x, contains("msg")) %>%
  mutate(type = gsub("msg_rel_", "", type),
         group = ifelse(group == 0, "broadcast", "narrowcast")) %>%
  extract(type, c("variable", "type"), "(.*)_(.*)") %>%
  filter(x < 3 & x > -3)

predicted %>%
  mutate(group = ifelse(group == 0, "broadcast", "narrowcast")) %>%
  extract(type, c("variable", "type"), "(.*)_(.*)") %>%
  ggplot(aes(x, predicted, color = group, fill = group, linetype = type)) +
  geom_point(data = points, aes(x, predicted), alpha = .02, size = .25) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2, color = NA) +
  geom_line(size = 1) +
  facet_grid(~variable) +
  scale_color_manual(name = "", values = palette_sharing) +
  scale_fill_manual(name = "", values = palette_sharing) +
  scale_linetype_manual(name = "", values = c("solid", "dashed")) +
  guides(linetype = guide_legend(override.aes = list(fill = NA))) +
  labs(x = "\nstandardized relevance rating", y = "predicted standardized sharing intention rating\n") +
  plot_aes  +
  theme(legend.position = "top",
        legend.key.width=unit(2,"cm"))
```

### model summary table
```{r}
model %>%
  broom.mixed::tidy(conf.int = TRUE) %>%
  filter(effect == "fixed") %>%
  rename("SE" = std.error,
         "t" = statistic,
         "p" = p.value) %>%
  select(-group, -effect) %>%
  mutate_at(vars(-contains("term"), -contains("p.value")), round, 2) %>%
  mutate(term = gsub(":", " x ", term),
         term = gsub("msg_", "", term),
         term = gsub("_", " ", term),
         term = gsub("within", "within", term),
         term = gsub("between", "between", term),
         term = gsub("rel self", "self relevance", term),
         term = gsub("rel social", "social relevance", term),
         term = gsub("sharing type", "sharing type (narrowcast)", term),
         p = ifelse(p < .001, "< .001",
                    ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
         `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high)) %>%
  select(term, `b [95% CI]`, df, t, p) %>%
  kable()  %>%
  kableExtra::kable_styling()
```

# person-level {.tabset}
In these analyses, select a subset of people that have correlations between self and social relevance < .7.

Because participants tended to only rate a few messages, this approach to downsampling is likely more unstable. Therefore, these analyses are supplementary and not reported in the manuscript.

## correlations {.tabset}
### descriptives {.tabset}
Describe the correlations between self and social relevance by study and content type.

#### across content
```{r}
cors_spread = merged %>%
  ungroup() %>%
  select(study, SID, msg_rel_self, msg_rel_social) %>%
  unique()

cors = cors_spread %>%
  nest(-c(study, SID)) %>%
  mutate(test = map(data, possibly(~ cor.test(.$msg_rel_self, .$msg_rel_social), otherwise = NULL))) %>%
  filter(!test == "NULL") %>%
  mutate(coefs = map(test,
                     broom::tidy,
                     conf.int = TRUE,
                     conf.level = .95)) %>% 
  unnest(coefs, .drop = TRUE) %>%
  mutate_if(is.numeric, round, 2)

cors %>%
  group_by(study) %>%
  summarize(`mean correlation` = mean(estimate, na.rm = TRUE),
            `sd correlation` = sd(estimate, na.rm = TRUE),
            min = min(estimate, na.rm = TRUE),
            max = max(estimate, na.rm = TRUE)) %>%
  mutate(`range correlation` = sprintf("%.2f, %.2f", min, max)) %>%
  select(-min, -max) %>%
  kable(digits = 2) %>%
  kableExtra::kable_styling()
```

### plot
```{r, fig.width=8, fig.height=5}
cors %>%
  arrange(study, SID) %>%
  mutate(item = row_number(),
         V1 = sprintf("self_%s", row_number()),
         V2 = sprintf("social_%s", row_number())) %>%
  ggplot(aes(item, estimate, color = study)) +
  geom_point() +
  geom_hline(yintercept = .7) +
  scale_color_manual(values = palette_study) +
  labs(x = "\nmessage number", y = "correlation between\nself and social relevance\n") +
  plot_aes +
  theme(legend.text = element_text(size = 11))
```

### number of messages per study with < .7 correlation
```{r}
data_lower_cors = cors %>%
  filter(estimate < .7)

total_n = merged %>%
  ungroup() %>%
  select(study, SID) %>%
  unique() %>%
  group_by(study) %>%
  summarize(`total n` = n())

data_lower_cors %>%
  group_by(study) %>%
  summarize(n = n()) %>%
  left_join(., total_n) %>%
  mutate(percent = (n / `total n`) * 100) %>%
  kable(digits = 2) %>%
  kableExtra::kable_styling()
```

## downsampled mega-analysis {.tabset}
Estimate the mega-analysis model in the downsampled dataset.

### run model
```{r}
data_downsample = merged %>%
  filter(SID %in% data_lower_cors$SID)

model = lmerTest::lmer(msg_share_std ~ 0 + msg_rel_self_between*sharing_type +
                                 msg_rel_self_within*sharing_type +
                                 msg_rel_social_between*sharing_type +
                                 msg_rel_social_within*sharing_type +
                                 (1 + msg_rel_self_within + msg_rel_social_within | SID) +
                                 (1 + msg_rel_self_within + msg_rel_social_within | item),
                               data = data_downsample,
                       control = lmerControl(optimizer = "bobyqa"))

car::vif(model)
```

### plot
```{r, fig.width=10, fig.height=6}
predicted = ggeffects::ggpredict(model, c("msg_rel_self_between [-3:3]", "sharing_type")) %>%
  data.frame() %>%
  mutate(type = "self_between") %>%
  bind_rows(ggeffects::ggpredict(model, c("msg_rel_self_within [-3:3]", "sharing_type")) %>%
              data.frame() %>%
              mutate(type = "self_within")) %>%
  bind_rows(ggeffects::ggpredict(model, c("msg_rel_social_between [-3:3]", "sharing_type")) %>%
              data.frame() %>%
              mutate(type = "social_between")) %>%
  bind_rows(ggeffects::ggpredict(model, c("msg_rel_social_within [-3:3]", "sharing_type")) %>%
              data.frame() %>%
              mutate(type = "social_within"))

points = data_downsample %>%
  select(-group) %>%
  rename("group" = sharing_type,
         "predicted" = msg_share_std) %>%
  select(study, SID, group, predicted, contains("within"), contains("between")) %>%
  gather(type, x, contains("msg")) %>%
  mutate(type = gsub("msg_rel_", "", type),
         group = ifelse(group == 0, "broadcast", "narrowcast")) %>%
  extract(type, c("variable", "type"), "(.*)_(.*)") %>%
  filter(x < 3 & x > -3)

(fig3_alt = predicted %>%
  mutate(group = ifelse(group == 0, "broadcast", "narrowcast")) %>%
  extract(type, c("variable", "type"), "(.*)_(.*)") %>%
  ggplot(aes(x, predicted, color = group, fill = group, linetype = type)) +
  geom_point(data = points, aes(x, predicted), alpha = .02, size = .25) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2, color = NA) +
  geom_line(size = 1) +
  facet_grid(~variable) +
  scale_color_manual(name = "", values = palette_sharing) +
  scale_fill_manual(name = "", values = palette_sharing) +
  scale_linetype_manual(name = "", values = c("solid", "dotted")) +
  guides(linetype = guide_legend(override.aes = list(fill = NA))) +
  labs(x = "\nstandardized relevance rating", y = "predicted standardized sharing intention rating\n") +
  plot_aes  +
  theme(legend.position = "top",
        legend.key.width=unit(2,"cm")))
```

### model summary table
```{r, fig.width=10, fig.height=4.5}
model %>%
  broom.mixed::tidy(conf.int = TRUE) %>%
  filter(effect == "fixed") %>%
  rename("SE" = std.error,
         "t" = statistic,
         "p" = p.value) %>%
  select(-group, -effect) %>%
  mutate_at(vars(-contains("term"), -contains("p.value")), round, 2) %>%
  mutate(term = gsub(":", " x ", term),
         term = gsub("msg_", "", term),
         term = gsub("_", " ", term),
         term = gsub("within", "within", term),
         term = gsub("between", "between", term),
         term = gsub("rel self", "self relevance", term),
         term = gsub("rel social", "social relevance", term),
         term = gsub("sharing type", "sharing type (narrowcast)", term),
         p = ifelse(p < .001, "< .001",
                    ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
         `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high)) %>%
  select(term, `b [95% CI]`, df, t, p) %>%
  kable()  %>%
  kableExtra::kable_styling()
```
