---
title: "Specification curve analyses"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(scipen = 999)
```

This document provides the code for the analyses reported in:

[Cosme et al. (Preprint) Message self and social relevance is positively related to sharing intentions:
Correlational and causal evidence from six studies]()


In these analyses, we assess the robustness of the relationships from the mega-analysis using specification curve analysis.

# prep data {.tabset}
First, we load the relevant packages and data, and define the plotting aesthetics.

## load packages
```{r}
if (!require(tidyverse)) {
  install.packages('tidyverse')
}
if (!require(lmerTest)) {
  install.packages('lmerTest')
}
if (!require(purrr)) {
  install.packages('purrr')
}
if (!require(furrr)) {
  install.packages('furrr')
}
if (!require(ggpubr)) {
  install.packages('ggpubr')
}
if (!require(combinat)) {
  install.packages('combinat')
}
devtools::install_github("dcosme/specr", ref = "plotmods")
if (!require(report)) {
  install.packages('report')
}
report::cite_packages()
```

## define aesthetics
```{r}
palette = c("#001219", "#005F73", "#0A9396", "#94D2BD", "#E9D8A6", "#EE9B00", "#CA6702", "#BB3E03", "#AE2012")
palette_sharing = c("#0a9396", "#EE9B00")
palette_relevance = c("#bb3e03", "#f14f04", "#005F73", "#0088a3")
palette_medium = c("#94d2bd", "#e9d8a6")
palette_decisions = c("#3B9AB2", "#EBCC2A", "#F21A00")

plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 12),
        text = element_text(size = 16, family = "Futura Medium"),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank())
```

## load and merge data
```{r}
# demographics
study1_demo = read.csv("../data/study1_demo.csv", stringsAsFactors = FALSE)

study2_demo = read.csv("../data/study2_demo.csv", stringsAsFactors = FALSE)

study3_demo = read.csv("../data/study3_demo.csv", stringsAsFactors = FALSE)

study4_demo = read.csv("../data/study4_demo.csv", stringsAsFactors = FALSE)

study5_demo = read.csv("../data/study5_demo.csv", stringsAsFactors = FALSE)

study6_demo = read.csv("../data/study6_demo.csv", stringsAsFactors = FALSE)

merged_demo = bind_rows(study1_demo, study2_demo, study3_demo, study4_demo, study5_demo, study6_demo) %>%
  spread(item, value) %>%
  select(-gender_4_TEXT, -race_self) %>%
  rename("SES_degree" = `highest degree completed`,
         "SES_income" = `household income`,
         "hispanic_latinx" = `Hispanic or Latinx`) %>%
  mutate(age = as.numeric(age))

# load and tidy study data
study1 = read.csv("../data/study1.csv", stringsAsFactors = FALSE)

study2 = read.csv("../data/study2.csv", stringsAsFactors = FALSE)

study3 = read.csv("../data/study3.csv", stringsAsFactors = FALSE)

study4 = read.csv("../data/study4.csv", stringsAsFactors = FALSE)

study5 = read.csv("../data/study5.csv", stringsAsFactors = FALSE)

study6 = read.csv("../data/study6.csv", stringsAsFactors = FALSE)

merged = bind_rows(study1, study2, study3, study4, study5, study6) %>%
  group_by(study, sharing_type) %>%
  mutate(msg_share_std = scale(msg_share, scale = TRUE, center = TRUE),
         medium = ifelse(grepl("1|2|3", study), "social media", "newspaper")) %>% 
  left_join(., merged_demo) %>%
  mutate(gender = as.factor(gender),
         hispanic_latinx = as.factor(hispanic_latinx),
         race = ifelse(race == "Hispanic" | race == "Latino", NA, race),
         race = as.factor(race),
         SES_degree = factor(SES_degree, ordered = TRUE,
                             levels = c("Less than high school", "High school graduate (diploma)",
                                        "High school graduate (GED)",
                                        "Some college (1-4 years, no degree)",
                                        "Associate's degree (including occupational or academic degrees)",
                                        "Bachelor's degree (BA, BS, etc)",
                                        "Master's degree (MA, MS, MENG, MSW, etc)",
                                        "Professional school degree (MD, DDC, JD, etc)",
                                        "Doctorate degree (PhD, EdD, etc)")),
         SES_income = factor(SES_income, ordered = TRUE,
                             levels = c("Less than $5,000",
                                        "$5,000 through $11,999",
                                        "$12,000 through $15,999",
                                        "$16,000 through $24,999",
                                        "$25,000 through $34,999",
                                        "$35,000 through $49,999",
                                        "$50,000 through $74,999",
                                        "$75,000 through $99,999",
                                        "$100,000 and greater")))
```

# prep for SCA {.tabset}
## define functions
These functions are adapted from the [specr package](https://masurp.github.io/specr/).

```{r}
# specr functions
convert_formula = function(x, y, controls, random_effects, ...) {
	if (controls == "no covariates") {
		paste(y, "~", x, "+", random_effects)    
	} else {
		paste(y, "~", x, "+", controls, "+", random_effects)
	}
}

run_spec <- function(specs, df, conf.level, keep.results = FALSE) {

  # dependencies
  require(dplyr)
  require(purrr)
  

  results <- specs %>%
    mutate(formula = pmap(., convert_formula)) %>%
    tidyr::unnest(formula) %>%
    mutate(res = map2(model, formula, possibly(~ do.call(.x, list(data = df,
                                                                  formula = .y,
                                                                  control = lmerControl(optimizer = "bobyqa"))),
                                               otherwise = NULL))) %>%
    filter(!res == "NULL") %>%
    mutate(coefs = map(res,
                       broom.mixed::tidy,
                       conf.int = TRUE,
                       conf.level = .95),
           obs = map(res, nobs)) %>%
    tidyr::unnest(coefs) %>%
    tidyr::unnest(obs) %>%
    filter(term == x) %>%
    select(-term)

  if (isFALSE(keep.results)) {
    results <- results %>%
      select(-res)
  }

  return(results)
}

create_subsets <- function(df, subsets) {

  # dependencies
  require(dplyr)

  subsets %>%
    stack %>%
    purrr::pmap(~ filter(df, get(as.character(..2)) == ..1) %>%
                  mutate(filter = paste(..2, "=", ..1)))
}
```

## tidy data
Define relevant variables and subset this data for modeling.

```{r}
# specify model components and variables
dvs = "msg_share_std"
ivs = c("msg_rel_self_between", "msg_rel_self_within", "msg_rel_social_between", "msg_rel_social_within")
controls = c("age", "gender", "SES_degree", "SES_income", "race", "hispanic_latinx", "")
model = "lmer"
random_effects = "(1 + msg_rel_self_within + msg_rel_social_within | SID) + (1 | item)"
conf_level = .95

# get relevant variables
model_df = merged %>%
  select(study, SID, item, content, sharing_type, medium, !!dvs, !!ivs, !!controls[1:6]) %>%
  mutate(sharing_type = ifelse(sharing_type == 0, "broadcast", "narrowcast"))
```

## generate model specifications from model components
```{r}
models = expand.grid(x = ivs,
										 y = dvs,
										 model = model,
										 controls = controls,
										 control_ivs = paste(ivs, collapse = " _ "),
										 random_effects = random_effects, stringsAsFactors = FALSE) %>%
  mutate(control_ivs = str_remove(control_ivs, x),
         control_ivs = str_replace(control_ivs, "^ _ ", ""),
         control_ivs = str_replace(control_ivs, " _ $", ""),
         control_ivs = str_replace(control_ivs, " _  _ ", " _ "),
         control_ivs = gsub(" _ ", " + ", control_ivs, fixed = TRUE),
         controls = ifelse(controls == "", control_ivs,
                           sprintf("%s + %s", control_ivs, controls))) %>%
  select(-control_ivs) %>%
  as_tibble()
```

## create subsets
Create subsets of the data to estimate the models within.

```{r}
# define subsets
subsets_1 = list(content = "covid",
                 sharing_type = "broadcast")
               
subsets_2 = list(sharing_type = unique(model_df$sharing_type),
                 medium = unique(model_df$medium))
               
subsets_3 = list(content = unique(model_df$content),
                 sharing_type = unique(model_df$sharing_type),
                 medium = unique(model_df$medium))

# create the subset dataframes if the models have not yet been run
if (!file.exists("models/sca_output_12.RDS")) {
  # broadcast covid
  subsets_1 = map(subsets_1, as.character)
  df_1 = subsets_1 %>%
      cross %>%
      map(~ create_subsets(subsets = .x, df = model_df) %>%
            map(~ dplyr::select(.x, -filter)) %>%
            reduce(dplyr::inner_join) %>%
            dplyr::mutate(filter = paste(names(.x),
                                         .x,
                                         collapse = " & ",
                                         sep = " = "))) %>%
    Filter(function(x) nrow(x) > 0, .) # filter out empty dataframes
  
  # medium, sharing type
  subsets_2 = map(subsets_2, as.character)
  df_2 = subsets_2 %>%
      cross %>%
      map(~ create_subsets(subsets = .x, df = model_df) %>%
            map(~ dplyr::select(.x, -filter)) %>%
            reduce(dplyr::inner_join) %>%
            dplyr::mutate(filter = paste(names(.x),
                                         .x,
                                         collapse = " & ",
                                         sep = " = "))) %>%
    Filter(function(x) nrow(x) > 0, .) %>% # filter out empty dataframes
    Filter(function(x) sum(x$filter == "sharing_type = narrowcast & medium = social media") == 0, .)

  # content, medium, sharing type
  subsets_3 = map(subsets_3, as.character)
  df_3 = subsets_3 %>%
      cross %>%
      map(~ create_subsets(subsets = .x, df = model_df) %>%
            map(~ dplyr::select(.x, -filter)) %>%
            reduce(dplyr::inner_join) %>%
            dplyr::mutate(filter = paste(names(.x),
                                         .x,
                                         collapse = " & ",
                                         sep = " = "))) %>%
    Filter(function(x) nrow(x) > 0, .) # filter out empty dataframes
  
# combine subsets 1 and 2 
  df_all = append(df_1, df_2) %>%
    append(., df_3)
}
```

# run SCA {.tabset}
## run models
Run models or load saved output from file.

```{r}
if (!file.exists("models/sca_output.RDS")) {
  # setup parallelization with furrr
  plan(multisession, workers = 10)
  
  # run SCA
  output = furrr::future_map_dfr(df_all, ~ run_spec(models, .x,
                                                    conf.level = conf_level,
                                                    keep.results = FALSE) %>%
                          mutate(subsets = unique(.x$filter)))
  # save output
  saveRDS(output, "models/sca_output.RDS")

} else {
  
  #load output
  output = readRDS("models/sca_output.RDS")
}
```

## tidy output
```{r}
output = bind_rows(output) %>%
  mutate(x = gsub("msg_rel_", "", x),
         x = gsub("_", " ", x),
         content = ifelse(grepl("covid", subsets), "COVID-19",
                   ifelse(grepl("voting", subsets), "voting",
                   ifelse(grepl("health", subsets), "health",
                   ifelse(grepl("climate", subsets), "climate",
                   ifelse(subsets == "sharing_type = broadcast & medium = social media", "COVID-19 & voting",
                   ifelse(subsets == "sharing_type = broadcast & medium = newspaper", "COVID-19, health & climate",  
                   ifelse(subsets == "sharing_type = narrowcast & medium = newspaper", "COVID-19 & climate", "all"))))))),
         `COVID-19` = ifelse(grepl("COVID-19", content), "COVID-19", NA),
         voting = ifelse(grepl("voting", content), "voting", NA),
         health = ifelse(grepl("health", content), "health", NA),
         climate = ifelse(grepl("climate", content), "climate", NA),
         sharing = ifelse(grepl("broad", subsets), "broadcast",
                  ifelse(grepl("narrow", subsets), "narrowcast", "all")),
         medium = ifelse(grepl("media", subsets), "social media",
                  ifelse(subsets == "content = covid & sharing_type = broadcast", "social media",
                  ifelse(grepl("news", subsets), "newspaper", "all"))),
         relevance = x,
         controls = ifelse(grepl("age|SES|race|hispanic", controls), "controls", "no controls"),
         subset = case_when(subsets == "content = covid & sharing_type = broadcast" ~ "10",
                                   subsets == "sharing_type = broadcast & medium = social media" ~ "11",
                                   subsets == "sharing_type = broadcast & medium = newspaper" ~ "12",
                                   subsets == "sharing_type = narrowcast & medium = newspaper" ~ "13",
                                   subsets == "content = covid & sharing_type = broadcast & medium = social media" ~ "1",
                                   subsets == "content = voting & sharing_type = broadcast & medium = social media" ~ "4",
                                   subsets == "content = voting & sharing_type = narrowcast & medium = social media" ~ "5",
                                   subsets == "content = covid & sharing_type = broadcast & medium = newspaper" ~ "2",
                                   subsets == "content = health & sharing_type = broadcast & medium = newspaper" ~ "6",
                                   subsets == "content = climate & sharing_type = broadcast & medium = newspaper" ~ "8",
                                   subsets == "content = covid & sharing_type = narrowcast & medium = newspaper" ~ "3",
                                   subsets == "content = health & sharing_type = narrowcast & medium = newspaper" ~ "7",
                                   subsets == "content = climate & sharing_type = narrowcast & medium = newspaper" ~ "9"))
```

# plot SCA {.tabset}
## decisions
This plot depicts the set of models run in each subset of the data. It is supplementary and does not appear in the manuscript.

```{r}
# define edges
l1 = expand.grid(from = dvs, to = ivs) %>%
  group_by(to) %>%
  mutate(key = "relevance variables",
         to = sprintf("%s_%s", to, row_number()))
l2 = expand.grid(from = unique(l1$to), to = controls) %>%
  group_by(to) %>%
  mutate(key = "control variables",
         to = sprintf("%s_%s", to, row_number()))
edge_list = bind_rows(l1, l2)

# plot
decision_plot = igraph::graph_from_data_frame(edge_list)

ggraph::ggraph(decision_plot, layout = 'dendrogram', circular = FALSE) + 
  ggraph::geom_edge_diagonal(aes(color = key), strength = 0) +
  ggraph::scale_edge_color_manual(name = "decision key", values = palette_decisions) +
  theme_void() +
  theme(legend.position = "top")
```

## define functions
### modified specr functions
These functions are adapted from the [specr package](https://masurp.github.io/specr/).

```{r}
format_results <- function(df, var, null = 0, desc = FALSE) {

  # rank specs
  if (isFALSE(desc)) {
    df <- df %>%
      dplyr::arrange(estimate)
  } else {
    df <- df %>%
      dplyr::arrange(desc(estimate))
  }

  # create rank variable and color significance
  df <- df %>%
    dplyr::mutate(specifications = 1:n(),
           color = case_when(conf.low > null ~ "black",
                             conf.high < null ~ "black",
                             TRUE ~ "darkgrey"))
  return(df)
}

plot_choices <- function(df,
                         var = .data$estimate,
                         choices = c("x", "y", "model", "controls", "subsets"),
                         desc = FALSE,
                         null = 0,
                         size = 5,
                         alpha_values = c(1, 1),
                         color_vars = NULL,
                         palette = NULL,
                         rename_controls = FALSE,
                         ignore_vars = FALSE,
                         collapse_content = FALSE) {

  value <- key <- NULL

  var <- enquo(var)
  
  if (collapse_content == TRUE) {
  
    df = df %>%
      format_results(var = var, null = null, desc = desc) %>%
      select(-content) %>%
      gather(content_type, content, `COVID-19`, voting, health, climate) %>%
      filter(!is.na(content)) %>%
      select(-content_type)
  
  } else {
    df = df %>%
      format_results(var = var, null = null, desc = desc)
  }

  if (!is.null(color_vars)) {
    color_num_key = df %>%
      select(!!color_vars) %>%
      unique() %>%
      arrange(get(color_vars)) %>%
      mutate(color_num = row_number())

    data_df = df %>%
      left_join(., color_num_key) %>%
      mutate(controls = ifelse(grepl("[+]", controls), "all covariates", controls),
             alpha = ifelse(color == "black", "yes", "no"),
             color = sprintf("%s", eval(parse(text = "palette[color_num]")))) %>%
      tidyr::gather(key, value, choices) %>%
      mutate(key = ifelse(isFALSE(rename_controls) == FALSE & key == "controls", rename_controls, key),
             value = ifelse(isFALSE(ignore_vars) == FALSE & value %in% ignore_vars, NA, value)) %>%
      filter(!is.na(value)) %>%
      unique() %>%
      mutate(key = factor(key, levels=unique(key)))

  } else {

    data_df = df %>%
      mutate(controls = ifelse(grepl("[+]", controls), "all covariates", controls)) %>%
      tidyr::gather(key, value, choices) %>%
      mutate(key = ifelse(isFALSE(rename_controls) == FALSE & key == "controls", rename_controls, key),
             value = ifelse(isFALSE(ignore_vars) == FALSE & value %in% ignore_vars, NA, value),
             alpha = "yes") %>%
      filter(!is.na(value)) %>%
      unique() %>%
      mutate(key = factor(key, levels=unique(key)))
  }

  data_df %>%
    ggplot(aes(x = .data$specifications,
               y = .data$value,
               color = .data$color)) +
    geom_point(aes(x = .data$specifications,
                   y = .data$value,
                   alpha = alpha),
               shape = 124,
               size = size) +
    scale_color_identity() +
    scale_alpha_manual(values = alpha_values) +
    theme_minimal() +
    facet_grid(.data$key~1, scales = "free_y", space = "free_y") +
    theme(
      axis.line = element_line("black", size = .5),
      legend.position = "none",
      panel.spacing = unit(.75, "lines"),
      axis.text = element_text(colour = "black"),
      strip.text.x = element_blank()) +
    labs(x = "", y = "")

}
```

### plotting functions
```{r}
plot_sca = function(data, combined = TRUE, labels = c("A", "B"),
                    title = FALSE, limits = NULL,
                    point_size = .5, point_alpha = 1,
                    ci = TRUE, ci_alpha = .5, ci_size = .5,
                    line = FALSE, line_size = 1,
                    median_alpha = 1, median_size = 1,
                    text_size = 14, title_size = 6,
                    color_vars = NULL, palette = palette, legend = TRUE,
                    choices  = c("x", "content", "medium", "sharing", "controls"),
                    alpha_values = c(0.5, 1),
                    remove_y = FALSE, remove_facet = FALSE,
                    collapse_content = FALSE) {
  
  medians = data %>%
    group_by(get(color_vars)) %>%
    summarize(median = median(estimate)) %>%
    ungroup() %>%
    mutate(color = sprintf("%s", palette))
  
  if (combined == TRUE) {
      p1 = specr::plot_curve(data, point_size = point_size, point_alpha = point_alpha,
                      ci = ci, ci_alpha = ci_alpha, ci_size = ci_size,
                      line = line, line_size = line_size,
                      limits = limits) +
        geom_hline(data = medians, aes(yintercept = median, color = color, linetype = `get(color_vars)`),
                   alpha = median_alpha, size = median_size, show_guide = TRUE) +
        scale_linetype_manual(name = "", values = rep(1, nrow(medians)), 
                              guide = guide_legend(override.aes = list(color = palette))) +
        labs(x = "", y = "standarized\nregression coefficient\n")  +
        theme(legend.position = "top",
              text = element_text(size = text_size, family = "Futura Medium"))
      
      if (legend == FALSE) {
        p1 = p1 +
          theme(legend.position = "none")
      }
      
      if (title == TRUE) {
        if (is.null(limits)) {
          title_range = max(data$conf.high) - min(data$conf.high)
          title_y = max(data$conf.high) - (title_range / 10)
        } else {
          title_range = limits[2] - limits[1]
          title_y = limits[2] - (title_range / 10)
        }
        p1 = p1 + annotate("text", -Inf, Inf, label = unique(data$x), fontface = 2, size = title_size,
                       x = 0.5*(1 + nrow(data)), 
                       y = title_y)
      }
      
      if (!is.null(color_vars)) {
        p2 = plot_choices(data, choices = choices,
                          alpha_values = alpha_values, color_vars = color_vars,
                          palette = palette, collapse_content = collapse_content) +
          labs(x = "\nspecifications (ranked)")  +
          theme(strip.text.x = element_blank(),
                text = element_text(size = text_size, family = "Futura Medium"))
      } else {
        p2 = plot_choices(data, choices = choices,
                          alpha_values = alpha_values, collapse_content = collapse_content) +
          labs(x = "\nspecifications (ranked)")  +
          theme(strip.text.x = element_blank(),
                text = element_text(size = text_size, family = "Futura Medium"))
      }
        
  } else {
      p1 = specr::plot_curve(data, point_size = point_size, point_alpha = point_alpha,
                      ci_alpha = ci_alpha, ci_size = ci_size) +
        geom_hline(yintercept = 0, linetype = "solid", color = "black", size = .5) +
        labs(x = "", y = "standarized\nregression coefficient\n") +
        theme(text = element_text(size = text_size, family = "Futura Medium"))
      
      if (title == TRUE) {
        if (is.null(limits)) {
          title_range = max(data$conf.high) - min(data$conf.high)
          title_y = max(data$conf.high) - (title_range / 10)
        } else {
          title_range = limits[2] - limits[1]
          title_y = limits[2] - (title_range / 10)
        }
        p1 = p1 + annotate("text", -Inf, Inf, label = unique(data$y), fontface = 2, size = title_size,
                       x = 0.5*(1 + nrow(data)), 
                       y = title_y)
      }
      
      p2 = plot_choices(data, choices = choices,
                               alpha_values = alpha_values, collapse_content = collapse_content) +
        labs(x = "\nspecification number (ranked)") +
        theme(strip.text.x = element_blank(),
              text = element_text(size = text_size, family = "Futura Medium"))
  }
  
  if (remove_y == TRUE) {
    p1 = p1 + labs(y = "")
    
    p2 = p2 + theme(axis.text.y = element_blank(),
                    axis.ticks.y = element_blank()) +
      labs(y = "")
  }

  if (remove_facet == TRUE) {
    p2 = p2 + theme(strip.text.y = element_blank())
  }
  
  specr::plot_specs(plot_a = p1,
             plot_b = p2,
             labels = labels,
             rel_height = c(.35, .65))
}

plot_sca_compare = function(data, pointrange = TRUE, labels = c("A", "B"), 
                            rel_heights = c(.75, .25), rel_widths = c(.75, .25), 
                            title = FALSE, text_size = 14, title_size = 6, n_rows = 1, angle_text = FALSE,
                            remove_x = FALSE, remove_y = FALSE, sig = NULL) {
  
  # source raincloud plot
  source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
  
  # merge and tidy for plotting
  plot_data = data %>%
    group_by(x) %>%
    arrange(estimate) %>%
    mutate(specification = row_number()) %>%
    ungroup() %>%
    unique()
  
  # labels
  median_cl_boot = function(x, conf = 0.95, df = TRUE, ci = "low") {
  
    lconf = (1 - conf)/2
    uconf = 1 - lconf
    require(boot)
    bmedian = function(x, ind) median(x[ind])
    bt = boot(x, bmedian, 1000)
    bb = boot.ci(bt, type = "perc")
    
    if (df == TRUE){
      data.frame(y = median(x),
                 ymin = quantile(bt$t, lconf), 
                 ymax = quantile(bt$t, uconf))
      
    } else {
      if (ci == "low") {
        quantile(bt$t, lconf)
      } else {
        quantile(bt$t, uconf)
      }
    }
  }
  
  labs = plot_data %>%
    group_by(x) %>%
    summarize(med = median(estimate),
              low = median_cl_boot(estimate, df = FALSE, ci = "low"),
              high = median_cl_boot(estimate, df = FALSE, ci = "high")) %>%
    mutate(range = max(high) - min(low),
           estimate = ifelse(med > 0, high + (range / 10), low - (range / 10)),
           label = ifelse(x %in% sig, "*", ""))
  
  # plot curves
  if (pointrange == TRUE) {
    a = plot_data %>%
    ggplot(aes(specification, estimate, color = x)) +
      geom_linerange(aes(ymin = conf.low, ymax = conf.high), size = .1) +
      geom_point() +
      geom_hline(yintercept = 0, linetype = "solid", color = "black", size = 1) +
      scale_color_manual(name = "", values = palette_relevance) +
      scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) + 
      labs(x = "\nspecification number (ranked)", y = "standarized\negression coefficient\n") + 
      theme_minimal() + 
      theme(strip.text = element_blank(), 
            axis.line = element_line("black", size = 0.5), 
            legend.position = c(.5, .1), 
            legend.direction = "horizontal",
            panel.spacing = unit(0.75, "lines"), 
            axis.text = element_text(colour = "black"),
            text = element_text(size = text_size, family = "Futura Medium"))
    if (title == TRUE) {
      a = a + annotate("text", -Inf, Inf, label = unique(plot.data$y), fontface = 2, size = title_size,
                       x = 0.5*(min(plot.data$specification) + max(plot.data$specification)), 
                       y = max(plot.data$conf.high))
    }
    
  } else {
    a = plot_data %>%
      ggplot(aes(specification, estimate, color = x)) +
      geom_point() +
      geom_hline(yintercept = 0, linetype = "solid", color = "black", size = 1) +
      scale_color_manual(name = "", values = palette_relevance) +
      scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) + 
      labs(x = "\nspecification number (ranked)", y = "standarized\nregression coefficient\n") + 
      theme_minimal() + 
      theme(strip.text = element_blank(), 
            axis.line = element_line("black", size = 0.5), 
            legend.position = "none", 
            legend.direction = "horizontal",
            panel.spacing = unit(0.75, "lines"), 
            axis.text = element_text(colour = "black"),
            text = element_text(size = text_size, family = "Futura Medium"))
    if (title == TRUE) {
      a = a + annotate("text", -Inf, Inf, label = unique(plot.data$y), fontface = 2, size = title_size,
                       x = 0.5*(min(plot.data$specification) + max(plot.data$specification)), 
                       y = max(plot.data$estimate))    
      }
  }
  
    b = plot_data %>%
      group_by(x) %>%
      mutate(order = median(estimate)) %>%
      ggplot(aes(reorder(x, order), estimate, fill = x)) +
      geom_flat_violin(position = position_nudge(x = .1, y = 0), color = FALSE) +
      geom_point(aes(color = x), position = position_jitter(width = .05), size = .5, alpha = .5) + 
      geom_boxplot(width = .1, outlier.shape = NA, fill = NA) +
      geom_text(data = labs, aes(label = label, x = x, y = estimate), size = 6) +
      scale_fill_manual(name = "", values = palette_relevance) +
      scale_color_manual(name = "", values = palette_relevance) +
      scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) + 
      labs(x = "\n", y = "standarized\nregression coefficient\n") + 
      theme_minimal() + 
      theme(strip.text = element_blank(), 
            axis.line = element_line("black", size = 0.5), 
            legend.position = "none", 
            panel.spacing = unit(0.75, "lines"), 
            axis.text = element_text(colour = "black"),
            text = element_text(size = text_size, family = "Futura Medium"))
    
    if (angle_text == TRUE) {
      b = b + theme(axis.text.x = element_text(angle = 45, hjust = 1))
    }
    
  if (n_rows == 1) {
    a = a + theme(legend.position = c(.5, .1))
    b = b + coord_flip() +
      labs(x = "\n", y = "\nmedian") + 
      theme(axis.text.x = element_text(angle = 0, hjust = 1),
            axis.text.y = element_blank())
  }     
    

  if (remove_x == TRUE) {
    a = a + labs(x = "")
    
    if (n_rows == 1) {
      b = b + labs(y = "")
    } else {
      b = b + labs(x = "")
    }
  }    
  
  if (remove_y == TRUE) {
    a = a + labs(y = "")
    
    if (n_rows == 1) {
      b = b + labs(x = "")
    } else {
      b = b + labs(y = "")
    }
  }  
    
  cowplot::plot_grid(a, b, labels = labels, rel_heights = rel_heights, rel_widths = rel_widths, nrow = n_rows)
}
```

## main manuscript plot
This plot is reported in Figure 3.
```{r, fig.width=14, fig.height=16}
self_between = plot_sca(data = filter(output, grepl("self between", x)), combined = TRUE, title = TRUE,
         ci_alpha = 1, alpha_values = c(1, 1), text_size = 18,
         color_vars = "medium", palette = palette_medium,
         remove_facet = TRUE, labels = c("", ""), median_size = .75,
         choices = c("content", "medium", "sharing", "controls"), limits = c(-.3, 1),
         collapse_content = TRUE)

social_between = plot_sca(data = filter(output, grepl("social between", x)), combined = TRUE, title = TRUE,
         ci_alpha = 1, alpha_values = c(.5, 1), text_size = 18,
         color_vars = "medium", palette = palette_medium,
         remove_y = TRUE, labels = c("", ""), median_size = .75,
         choices = c("content", "medium", "sharing", "controls"), limits = c(-.3, 1),
         collapse_content = TRUE)

self_within = plot_sca(data = filter(output, grepl("self within", x)), combined = TRUE, title = TRUE,
         ci_alpha = 1, alpha_values = c(1, 1), text_size = 18,
         color_vars = "sharing", palette = palette_sharing,
         remove_facet = TRUE, labels = c("", ""), median_size = .75,
         choices = c("content", "medium", "sharing", "controls"), limits = c(-0, .4),
         collapse_content = TRUE)

social_within = plot_sca(data = filter(output, grepl("social within", x)), combined = TRUE, title = TRUE,
         ci_alpha = 1, alpha_values = c(1, 1), text_size = 18,
         color_vars = "sharing", palette = palette_sharing,
         remove_y = TRUE, labels = c("", ""), median_size = .75,
         choices = c("content", "medium", "sharing", "controls"), limits = c(-0, .4),
         collapse_content = TRUE)

ggarrange(self_between, social_between, self_within, social_within, 
          ncol = 2, nrow = 2, labels = c("A", "B", "C", "D"), widths = c(.51, .49, .51, .49))
```

## supplementary material plots {.tabset}
### combined
This plot is reported in Figure S5.

```{r, fig.width=12, fig.height=14}
plot_sca(data = output, combined = TRUE, title = FALSE, text_size = 20, median_size = 1.25,
         color_vars = "x", palette = palette_relevance, alpha_values = c(.2, .5),
         choices = c("relevance", "content", "medium", "sharing", "controls"),
         collapse_content = TRUE)
```

### include subsets {.tabset}
#### between-person relevance
This plot is reported in Figure S3.

```{r, fig.width=14, fig.height=14}
self_between_subset = plot_sca(data = filter(output, grepl("self between", x)), combined = TRUE, title = TRUE,
         ci_alpha = 1, alpha_values = c(1, 1), text_size = 18,
         color_vars = "medium", palette = palette_medium,
         remove_facet = TRUE, labels = c("", ""), median_size = .75,
         choices = c("content", "medium", "sharing", "controls", "subset"), limits = c(-.3, 1),
         collapse_content = TRUE)

social_between_subset= plot_sca(data = filter(output, grepl("social between", x)), combined = TRUE, title = TRUE,
         ci_alpha = 1, alpha_values = c(.5, 1), text_size = 18,
         color_vars = "medium", palette = palette_medium,
         remove_y = TRUE, labels = c("", ""), median_size = .75,
         choices = c("content", "medium", "sharing", "controls", "subset"), limits = c(-.3, 1),
         collapse_content = TRUE)

ggarrange(self_between_subset, social_between_subset, ncol = 2, labels = c("A", "B"), widths = c(.51, .49))
```

#### within-person relevance
This plot is reported in Figure S4.

```{r, fig.width=14, fig.height=14}
self_within_subset = plot_sca(data = filter(output, grepl("self within", x)), combined = TRUE, title = TRUE,
         ci_alpha = 1, alpha_values = c(1, 1), text_size = 18,
         color_vars = "sharing", palette = palette_sharing,
         remove_facet = TRUE, labels = c("", ""), median_size = .75,
         choices = c("content", "medium", "sharing", "controls", "subset"), limits = c(-0, .4),
         collapse_content = TRUE)

social_within_subset = plot_sca(data = filter(output, grepl("social within", x)), combined = TRUE, title = TRUE,
         ci_alpha = 1, alpha_values = c(1, 1), text_size = 18,
         color_vars = "sharing", palette = palette_sharing,
         remove_y = TRUE, labels = c("", ""), median_size = .75,
         choices = c("content", "medium", "sharing", "controls", "subset"), limits = c(-0, .4),
         collapse_content = TRUE)

ggarrange(self_within_subset, social_within_subset, ncol = 2, labels = c("A", "B"), widths = c(.51, .49))
```

## curve comparison
This plot is reported in Figure 2.

```{r, fig.width=6, fig.height=6}
plot_sca_compare(data = output, pointrange = FALSE, n_rows = 2, rel_heights = c(.5, .5))
```

# tables {.tabset}
Descriptive stats for the curve of each relevance variable.

## combined
This table is reported in Table 4.

```{r}
n_models = output %>%
  filter(relevance == "self within")

output %>%
  mutate(positive = ifelse(estimate > 0, 1, 0),
         negative = ifelse(estimate < 0, 1, 0),
         sig = case_when(conf.low > 0 ~ 1,
                             conf.high < 0 ~ 1,
                             TRUE ~ 0),
         positive_significant = ifelse(positive == 1 & sig == 1, 1, 0),
         negative_significant = ifelse(negative == 1 & sig == 1, 1, 0)) %>%
  group_by(relevance) %>%
  summarize(min = min(estimate),
            max = max(estimate),
            median = median(estimate),
            positive = (sum(positive) / nrow(n_models)) * 100,
            negative = (sum(negative) / nrow(n_models)) * 100,
            positive_significant = (sum(positive_significant) / nrow(n_models)) * 100,
            negative_significant = (sum(negative_significant) / nrow(n_models)) * 100) %>%
  mutate(range = sprintf("%.2f, %.2f", min, max)) %>%
  select(relevance, median, range, positive, negative, positive_significant, negative_significant) %>%
  knitr::kable(digits = 2)
```

## by sharing type
This table is reported in Table S4.

```{r}
n_broadcast = output %>%
  filter(sharing == "broadcast") %>%
  filter(relevance == "self between")

n_narrowcast = output %>%
  filter(sharing == "narrowcast") %>%
  filter(relevance == "self between")

output %>%
  mutate(positive = ifelse(estimate > 0, 1, 0),
         negative = ifelse(estimate < 0, 1, 0),
         sig = case_when(conf.low > 0 ~ 1,
                             conf.high < 0 ~ 1,
                             TRUE ~ 0),
         positive_significant = ifelse(positive == 1 & sig == 1, 1, 0),
         negative_significant = ifelse(negative == 1 & sig == 1, 1, 0)) %>%
  group_by(relevance, sharing) %>%
  summarize(min = min(estimate),
            max = max(estimate),
            median = median(estimate),
            positive = sum(positive),
            negative = sum(negative),
            positive_significant = sum(positive_significant),
            negative_significant = sum(negative_significant)) %>%
  gather(item, value, contains("positive"), contains("negative")) %>%
  mutate(value = ifelse(sharing == "broadcast", (value / nrow(n_broadcast)) * 100, (value / nrow(n_narrowcast)) * 100),
         range = sprintf("%.2f, %.2f", min, max)) %>%
  spread(item, value) %>%
  select(sharing, relevance, median, range, positive, negative, positive_significant, negative_significant) %>%
  knitr::kable(digits = 2)
```

## by message medium
This table is reported in Table S4.

```{r}
n_social = output %>%
  filter(medium == "social media") %>%
  filter(relevance == "self between")

n_newspaper = output %>%
  filter(medium == "newspaper") %>%
  filter(relevance == "self between")

output %>%
  mutate(positive = ifelse(estimate > 0, 1, 0),
         negative = ifelse(estimate < 0, 1, 0),
         sig = case_when(conf.low > 0 ~ 1,
                             conf.high < 0 ~ 1,
                             TRUE ~ 0),
         positive_significant = ifelse(positive == 1 & sig == 1, 1, 0),
         negative_significant = ifelse(negative == 1 & sig == 1, 1, 0)) %>%
  group_by(relevance, medium) %>%
  summarize(min = min(estimate),
            max = max(estimate),
            median = median(estimate),
            positive = sum(positive),
            negative = sum(negative),
            positive_significant = sum(positive_significant),
            negative_significant = sum(negative_significant)) %>%
  gather(item, value, contains("positive"), contains("negative")) %>%
  mutate(value = ifelse(medium == "social media", (value / nrow(n_social)) * 100, (value / nrow(n_newspaper)) * 100),
         range = sprintf("%.2f, %.2f", min, max)) %>%
  spread(item, value) %>%
  select(medium, relevance, median, range, positive, negative, positive_significant, negative_significant) %>%
  knitr::kable(digits = 2)
```

