---
title: "Study 4 Prep"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(scipen=999)
```

This document provides the code for the analyses reported in:

[Cosme et al. (Preprint) Message self and social relevance is positively related to sharing intentions:
Correlational and causal evidence from six studies]()

This script tidies and prepares the cleaned data from Study 4.

# load packages
```{r}
if(!require('pacman')) {
	install.packages('pacman')
}

pacman::p_load(tidyverse)
```

# load and tidy message data

Create disaggregated dataset

* Between-person variables are grand mean centered and standardized across people
* Within-person variables are centered within-person and standardized across people

```{r}
data_raw = read.csv("../data/study4_clean_long.csv", stringsAsFactors = FALSE)

ids = data_raw %>%
  select(ResponseId) %>%
  unique() %>%
  mutate(SID = sprintf("s%03d", row_number()))

data = data_raw %>%
  left_join(., ids) %>%
  select(-ResponseId)

between_subs = data %>%
  group_by(scale_name, SID) %>%
  summarize(value_between = mean(value, na.rm = TRUE)) %>%
  group_by(scale_name) %>%
  mutate(value_between = scale(value_between, scale = TRUE, center = TRUE),
         scale_name_between = sprintf("%s_between", scale_name)) %>%
  ungroup() %>%
  select(-scale_name) %>%
  spread(scale_name_between, value_between)

within_subs = data %>%
  group_by(scale_name, SID) %>%
  mutate(trial = row_number(),
         value_within = scale(value, scale = FALSE, center = TRUE),
         scale_name_within = sprintf("%s_within", scale_name)) %>%
  group_by(scale_name) %>%
  mutate(value_sd = sd(value_within, na.rm = TRUE),
         value_within = value_within / value_sd) %>%
  ungroup() %>%
  select(-value, -value_sd, -scale_name) %>%
  spread(scale_name_within, value_within)

data_mod_diss = data %>%
  group_by(scale_name, SID) %>%
  mutate(trial = row_number()) %>%
  spread(scale_name, value) %>%
  left_join(., between_subs) %>%
  left_join(., within_subs) %>%
  ungroup() %>%
  mutate(SID = as.factor(SID)) %>%
  unique() %>%
  mutate(study = "study 4",
         sharing_type = 0,
         group = "none",
         item = sprintf("%s_%s", study, item),
         SID = sprintf("%s_%s", study, SID),
         content = "health") %>%
  select(study, group, SID, item, content, trial, sharing_type, msg_share, contains("rel_"))
```

# tidy demographic data
```{r, eval = FALSE}
demo = data %>%
  select(SID, age, gender) %>%
  mutate(study = "study 4",
         SID = sprintf("%s_%s", study, SID),
         gender = ifelse(gender == "Male", "Man",
                  ifelse(gender == "Female", "Woman", NA))) %>%
  gather(item, value, -SID, -study) %>%
  unique()
```

# write csvs
```{r}
write.csv(data_mod_diss, "../data/study4.csv", row.names = FALSE)
write.csv(demo, "../data/study4_demo.csv", row.names = FALSE)
```
