---
title: "Study 5 Prep"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(scipen=999)
```

This document provides the code for the analyses reported in:

[Cosme et al. (Preprint) Message self and social relevance is positively related to sharing intentions:
Correlational and causal evidence from six studies]()

This script tidies and prepares the cleaned data from Study 5.

# load packages
```{r}
if(!require('pacman')) {
	install.packages('pacman')
}

pacman::p_load(tidyverse)
```

# load and tidy message data

Create disaggregated dataset

* Between-person variables are grand mean centered and standardized across people
* Within-person variables are centered within-person and standardized across people

```{r}
data_raw = read.csv("../data/study5_clean_long.csv", stringsAsFactors = FALSE)

articles = read.csv("../../correlational_study/articles.csv", stringsAsFactors = FALSE) %>%
  bind_cols(., data.frame(content = rep(c("covid", "climate"), 55))) %>%
  mutate(article_number = row_number()-1)

stim_order = data_raw %>%
  filter(grepl("stim_order", survey_name)) %>%
  select(SID, value) %>%
  mutate(article_number = strsplit(value, ",")) %>%
  unnest(article_number) %>%
  mutate(article_number = as.numeric(article_number)) %>%
  select(-value) %>%
  bind_cols(., data.frame(item = rep(1:10, length(unique(data_raw$SID))))) %>%
  mutate(item = as.character(item)) %>%
  left_join(., select(articles, article_number, content))

messages = data_raw %>%
  filter(grepl("sharing|relevance_self|relevance_social", survey_name)) %>%
  extract(item, "item", "([0-9]+)_.*") %>%
  mutate(value = as.numeric(value),
         survey_name = gsub("relevance", "rel", survey_name),
         survey_name = sprintf("msg_%s", survey_name)) %>%
  left_join(., stim_order)

between = messages %>%
  group_by(survey_name, SID) %>%
  summarize(value_between = mean(value, na.rm = TRUE)) %>%
  group_by(survey_name) %>%
  mutate(value_between = scale(value_between, scale = TRUE, center = TRUE),
         survey_between = sprintf("%s_between", survey_name)) %>%
  ungroup() %>%
  select(-survey_name) %>%
  spread(survey_between, value_between)

within = messages %>%
  group_by(survey_name, SID) %>%
  mutate(trial = row_number(),
         value_within = scale(value, scale = FALSE, center = TRUE),
         survey_name_within = sprintf("%s_within", survey_name)) %>%
  group_by(survey_name) %>%
  mutate(value_sd = sd(value_within, na.rm = TRUE),
         value_within = value_within / value_sd) %>%
  ungroup() %>%
  select(-value, -value_sd, -survey_name) %>%
  spread(survey_name_within, value_within)

data_mod_diss = messages %>%
  group_by(survey_name, SID) %>%
  mutate(trial = row_number()) %>%
  spread(survey_name, value) %>%
  left_join(., between) %>%
  left_join(., within) %>%
  ungroup() %>%
  mutate(SID = as.factor(SID)) %>%
  unique() %>%
  select(-msg_sharing_broad_between, -msg_sharing_broad_within, -msg_sharing_narrow_between, -msg_sharing_narrow_within) %>%
  gather(sharing_type, msg_share, contains("sharing")) %>%
  mutate(sharing_type = ifelse(sharing_type == "msg_sharing_broad", 0, 1)) %>%
  mutate(study = "study 5",
         group = "none",
         item = sprintf("%s_%s", content, article_number),
         SID = sprintf("%s_%s", study, SID)) %>%
  select(study, group, SID, item, content, trial, sharing_type, msg_share, contains("rel_"))
```

# tidy demographic data
```{r}
demo = data_raw %>%
  filter(grepl("gender|race|hispanic_latinx|ses_degree|income_household|^age$|state", item)) %>%
  ungroup() %>%
  select(SID, item, value) %>%
  mutate(value = ifelse(grepl("hispanic_latinx", item), recode(value, "1" = "Yes", "0" = "No"), value),
         value = ifelse(grepl("gender", item), recode(value, "1" = "Man", "2" = "Non-binary / third gender", "3" = "Woman", 
                                                      "4" = "Prefer to self-describe", "5" = "Prefer not to say"), value),
         value = ifelse(grepl("race", item), recode(value, "1" = "White", "2" = "Black or African American", 
                                                    "3" = "Asian", "4" = "American Indian or Alaskan Native", 
                                                    "5" = "Native Hawaiian or Other Pacific Islander",
                                                    "6" = "More than one race", "7" = "Prefer not to say"), value),
         value = ifelse(grepl("degree", item), recode(value, "1" = "Less than high school", "2" = "High school graduate (diploma)", 
                                                    "3" = "High school graduate (GED)", "4" = "Some college (1-4 years, no degree)", 
                                                    "5" = "Associate's degree (including occupational or academic degrees)", 
                                                    "6" = "Bachelor's degree (BA, BS, etc)",
                                                    "7" = "Master's degree (MA, MS, MENG, MSW, etc)",
                                                    "8" = "Professional school degree (MD, DDC, JD, etc)",
                                                    "9" = "Doctorate degree (PhD, EdD, etc)"), value),
         value = ifelse(grepl("household", item), recode(value, "1" = "Less than $5,000", "2" = "$5,000 through $11,999", 
                                                    "3" = "$12,000 through $15,999", "4" = "$16,000 through $24,999", 
                                                    "5" = "$25,000 through $34,999", "6" = "$35,000 through $49,999",
                                                    "7" = "$50,000 through $74,999", "8" = "$75,000 through $99,999",
                                                    "9" = "$100,000 and greater", "10" = "NA", "11" = "NA"), value),
         item = gsub("ses_income_household", "household income", item),
         item = gsub("ses_degree", "highest degree completed", item),
         value = gsub("Alaska ", "Alaskan ", value),
         item = gsub("hispanic_latinx", "Hispanic or Latinx", item)) %>%
  spread(item, value) %>%
  mutate(race = ifelse(is.na(race), race_self, race),
         gender = ifelse(gender == "Prefer to self-describe", gender_4_TEXT, gender),
         study = "study 5",
         SID = sprintf("%s_%s", study, SID)) %>%
  gather(item, value, -SID, -study)
```

# write csvs
```{r}
write.csv(data_mod_diss, "../data/study5.csv", row.names = FALSE)
write.csv(demo, "../data/study5_demo.csv", row.names = FALSE)
```

