---
title: "Study 1 Prep"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(scipen=999)
```

This document provides the code for the analyses reported in:

[Cosme et al. (Preprint) Message self and social relevance is positively related to sharing intentions:
Correlational and causal evidence from six studies]()

This script tidies and prepares the cleaned data from Study 1.

# load packages
```{r}
if(!require('pacman')) {
	install.packages('pacman')
}

pacman::p_load(tidyverse)
```

# load and tidy message data

Create disaggregated dataset

* Between-person variables are grand mean centered and standardized across people
* Within-person variables are centered within-person and standardized across people

```{r}
data_raw = read.csv("../data/study1a_clean_long.csv",
                    stringsAsFactors = FALSE) %>%
  bind_rows(read.csv("../data/study1b_clean_long.csv",
                     stringsAsFactors = FALSE)) %>%
  bind_rows(read.csv("../data/study1c_clean_long.csv",
                     stringsAsFactors = FALSE)) %>%
  bind_rows(read.csv("../data/study1d_clean_long.csv",
                     stringsAsFactors = FALSE) %>%
              mutate(study = "humor")) %>%
  mutate(condition = ifelse(condition == "fact-based", "control",
                     ifelse(condition == "encouraging", "non-mocking", condition)),
         group = ifelse(is.na(group), condition, group),
         group = ifelse(group == "message control", "control", 
                 ifelse(group == "encouraging", "non-mocking", group))) %>% 
  mutate(SID = sprintf("%s_%s", study, SID)) %>%
  filter(!group == "no message control") %>%
  select(-condition) %>%
  rename("scale_name" = survey_name)

messages = data_raw %>%
  filter(grepl("msg", scale_name)) %>%
  filter(scale_name %in% c("msg_rel_social", "msg_rel_self", "msg_share")) %>%
  extract(item, "item", ".*_([0-9]+)") %>%
  mutate(value = as.numeric(value),
         item = as.numeric(item))

between = messages %>%
  group_by(scale_name, SID) %>%
  summarize(value_between = mean(value, na.rm = TRUE)) %>%
  group_by(scale_name) %>%
  mutate(value_between = scale(value_between, scale = TRUE, center = TRUE),
         scale_name_between = sprintf("%s_between", scale_name)) %>%
  ungroup() %>%
  select(-scale_name) %>%
  spread(scale_name_between, value_between)

within = messages %>%
  group_by(scale_name, SID) %>%
  mutate(trial = row_number(),
         value_within = scale(value, scale = FALSE, center = TRUE),
         scale_name_within = sprintf("%s_within", scale_name)) %>%
  group_by(scale_name) %>%
  mutate(value_sd = sd(value_within, na.rm = TRUE),
         value_within = value_within / value_sd) %>%
  ungroup() %>%
  select(-value, -value_sd, -scale_name) %>%
  spread(scale_name_within, value_within)

data_mod_diss = messages %>%
  group_by(scale_name, SID) %>%
  mutate(trial = row_number()) %>%
  group_by(scale_name) %>%
  spread(scale_name, value) %>%
  left_join(., between) %>%
  left_join(., within) %>%
  ungroup() %>%
  mutate(SID = as.factor(SID)) %>%
  unique() %>%
  mutate(study = "study 1",
         sharing_type = 0,
         item = sprintf("%s_%s_%s", study, group, item),
         content = "covid") %>%
  select(study, group, SID, item, content, trial, sharing_type, msg_share, contains("rel_"))
```

# tidy demographic data
```{r}
demo = read.csv("../data/study1a_clean_long_demo.csv",
                    stringsAsFactors = FALSE) %>%
  bind_rows(read.csv("../data/study1b_clean_long_demo.csv",
                     stringsAsFactors = FALSE)) %>%
  bind_rows(read.csv("../data/study1c_clean_long_demo.csv",
                     stringsAsFactors = FALSE)) %>%
  bind_rows(read.csv("../data/study1d_clean_long_demo.csv",
                     stringsAsFactors = FALSE) %>%
              mutate(study = "humor")) %>%
  mutate(SID = sprintf("%s_%s", study, SID)) %>%
  rename("scale_name" = survey_name) %>%
  filter(grepl("gender|race|hispanic_latino|ses_degree|income_household|^age$|state", item)) %>%
  ungroup() %>%
  select(SID, item, value) %>%
  mutate(value = ifelse(grepl("hispanic_latino", item), recode(value, "1" = "Yes",
                                                               "0" = "No"), value),
         value = ifelse(grepl("gender", item), recode(value, "1" = "Man",
                                                      "2" = "Woman",
                                                      "3" = "Other",
                                                      "4" = "Prefer not to say",
                                                      "Would rather not say" = "Prefer not to say"), value),
         value = ifelse(grepl("race", item), recode(value, "1" = "White",
                                                    "2" = "Black or African American", 
                                                    "3" = "Asian",
                                                    "4" = "American Indian or Alaskan Native", 
                                                    "5" = "Native Hawaiian or Other Pacific Islander",
                                                    "6" = "Other"), value),
         value = ifelse(grepl("degree", item), recode(value, "1" = "Less than high school", "2" = "High school graduate (diploma)", 
                                                    "3" = "High school graduate (GED)", "4" = "Some college (1-4 years, no degree)", 
                                                    "5" = "Associate's degree (including occupational or academic degrees)", 
                                                    "6" = "Bachelor's degree (BA, BS, etc)",
                                                    "7" = "Master's degree (MA, MS, MENG, MSW, etc)",
                                                    "8" = "Professional school degree (MD, DDC, JD, etc)",
                                                    "9" = "Doctorate degree (PhD, EdD, etc)"), value),
         value = ifelse(grepl("household", item), recode(value, "1" = "Less than $5,000", "2" = "$5,000 through $11,999", 
                                                    "3" = "$12,000 through $15,999", "4" = "$16,000 through $24,999", 
                                                    "5" = "$25,000 through $34,999", "6" = "$35,000 through $49,999",
                                                    "7" = "$50,000 through $74,999", "8" = "$75,000 through $99,999",
                                                    "9" = "$100,000 and greater", "10" = "NA", "11" = "NA"), value),
         item = gsub("ses_income_household", "household income", item),
         item = gsub("ses_degree", "highest degree completed", item),
         value = gsub("Alaska ", "Alaskan ", value),
         item = gsub("hispanic_latino", "Hispanic or Latinx", item),
         value = ifelse(value == "Male", "Man",
                 ifelse(value == "Female", "Woman", value))) %>%
  spread(item, value) %>%
  mutate(race = ifelse(is.na(race), race_self, race),
         study = "study 1") %>%
  gather(item, value, -SID, -study)
```

# write csvs
```{r}
write.csv(data_mod_diss, "../data/study1.csv", row.names = FALSE)
write.csv(demo, "../data/study1_demo.csv", row.names = FALSE)
```

