---
title: "Study 2 Prep"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(scipen=999)
```

This document provides the code for the analyses reported in:

[Cosme et al. (Preprint) Message self and social relevance is positively related to sharing intentions:
Correlational and causal evidence from six studies]()

This script tidies and prepares the cleaned data from Study 2.

# load packages
```{r}
if(!require('pacman')) {
	install.packages('pacman')
}

pacman::p_load(tidyverse)
```

# load and tidy message data

Create disaggregated dataset

* Between-person variables are grand mean centered and standardized across people
* Within-person variables are centered within-person and standardized across people

```{r}
data_raw = read.csv("../data/study2_clean_long.csv", stringsAsFactors = FALSE)

messages = data_raw %>%
  filter(grepl("msg", scale_name)) %>%
  mutate(value = as.numeric(value)) %>%
  filter(scale_name %in% c("msg_rel_social", "msg_rel_self", "msg_share"))

between = messages %>%
  group_by(scale_name, SID) %>%
  summarize(value_between = mean(value, na.rm = TRUE)) %>%
  group_by(scale_name) %>%
  mutate(value_between = scale(value_between, scale = TRUE, center = TRUE),
         scale_name_between = sprintf("%s_between", scale_name)) %>%
  ungroup() %>%
  select(-scale_name) %>%
  spread(scale_name_between, value_between)

within = messages %>%
  group_by(scale_name, SID) %>%
  mutate(trial = row_number(),
         trial = ifelse(SID == "s055", as.numeric(item), trial),
         value_within = scale(value, scale = FALSE, center = TRUE),
         scale_name_within = sprintf("%s_within", scale_name),) %>%
  group_by(scale_name) %>%
  mutate(value_sd = sd(value_within, na.rm = TRUE),
         value_within = value_within / value_sd) %>%
  ungroup() %>%
  select(-value, -value_sd, -scale_name) %>%
  spread(scale_name_within, value_within)

data_mod_diss = messages %>%
  group_by(scale_name, SID) %>%
  mutate(trial = row_number(),
         trial = ifelse(SID == "s055", as.numeric(item), trial)) %>%
  group_by(scale_name) %>%
  spread(scale_name, value) %>%
  left_join(., between) %>%
  left_join(., within) %>%
  ungroup() %>%
  mutate(SID = as.factor(SID)) %>%
  unique() %>%
  mutate(study = "study 2",
         sharing_type = 0,
         item = sprintf("%s_%s_%s", study, group, item),
         SID = sprintf("%s_%s", study, SID),
         content = "voting") %>%
  select(study, group, SID, item, content, trial, sharing_type, msg_share, contains("rel_"))
```

# tidy demographic data
```{r}
demo = read.csv("../data/study2_clean_long_demo.csv", stringsAsFactors = FALSE) %>%
  filter(grepl("gender|race|hispanic_latinx|ses_degree|income_household|^age$", item)) %>%
  ungroup() %>%
  select(SID, item, value) %>%
  mutate(value = ifelse(grepl("hispanic_latinx", item), recode(value, "1" = "Yes", "0" = "No"), value),
         value = ifelse(grepl("gender", item), recode(value, "1" = "Man", "2" = "Non-binary / third gender", "3" = "Woman", 
                                                      "4" = "Prefer to self-describe", "5" = "Prefer not to say"), value),
         value = ifelse(grepl("race", item), recode(value, "1" = "White", "2" = "Black or African American", 
                                                    "3" = "Asian", "4" = "American Indian or Alaskan Native", 
                                                    "5" = "Native Hawaiian or Other Pacific Islander",
                                                    "6" = "More than one race", "7" = "Prefer not to say"), value),
         value = gsub("Alaska ", "Alaskan ", value),
         item = gsub("hispanic_latinx", "Hispanic or Latinx", item)) %>%
  spread(item, value) %>%
  mutate(race = ifelse(is.na(race), race_self, race),
         gender = ifelse(gender == "Prefer to self-describe", gender_4_TEXT, gender),
         study = "study 2",
         SID = sprintf("%s_%s", study, SID)) %>%
  gather(item, value, -SID, -study)
```

# write csvs
```{r}
write.csv(data_mod_diss, "../data/study2.csv", row.names = FALSE)
write.csv(demo, "../data/study2_demo.csv", row.names = FALSE)
```

